### 2012-12-03 write_up.tex
Added write up template / added latex files to .gitignore

\documentclass{article}

\title{Paper}
\author{T. Martian \& E. Brinkbot}

\begin{document}

\maketitle

\section{Complexity}

working on this section...

\end{document}

### 2012-12-03 write_up.tex
Did work on write up. Added Model section, Algorithm section, Complexity section

@@
 \documentclass{article}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
 
@@
 
+\section{Model}
+
+Model Description goes here...
+
+\begin{align*}
+  & k && \text{Number of blocks} \\
+  & \{s_i\}_{i=1..k} && \text{Number of nodes in each block}
+\end{align*}
+
+\section{Algorithm}
+
+The algorithm uses two lookup tables (one for the scheduler, and one
+for the nodes) to determine the optimal play given the relevant
+statistics of the game at decision time. Each table has a dimension
+for every relevant play statistic for the deciding agent, and contains
+their optimal choice as well as the expected number of Yeses in each
+block after that choice is made (which is necessary for callers to
+decide on their optimal decision, as expected payoffs are only a
+function of the expected number of Yeses at the end).
+
+These two tables back two oracles (wrong terminology?) which will
+return a precomputed value if it's already in the table, or they'll
+compute it as defined below. This can lead to a recursive cascade of
+computation, which is bounded by the size of the tables times the time
+to compute each element in terms of a lookup in one of them.
+
+We'll call the scheduler oracle
+\begin{align*}
+  & \operatorname{sched}(\{c_i\}, \{y_i\})
+  \intertext{and the node oracle}
+  & \operatorname{node}(t, b, \{c_i\}, \{y_i\})
+  \intertext{where}
+  & type && \text{Node's type (Yes or No)} \\
+  & n && \text{Node block} \\
+  & \{c_i\} && \text{Number of already chosen nodes by block} \\
+  & \{y_i\} && \text{Number of Yes chosen nodes by block}
+\end{align*}
+We can show (we need to show) that that's all of the relevant
+statistics either agent needs to know to determine a unique optimal
+decision.
+
+The scheduler just needs to check each possible choice of next block,
+and for each block calculate the expected number of Yeses by weighting
+the expected number of Yeses for a Yes or No node by the probability
+of a Yes or No node. This involves at most $2k$ calls to the node
+oracle, and is sufficient for determining the optimal choice of the
+scheduler.
+
+The nodes just have to find their expected value if they choose Yes or
+choose No. This is just comparing two calls to the sched oracle.
+
+Combining these two yields a polynomial in $n$ time algorithm for
+solving arbitrary block models.
+
 \section{Complexity}
 
-working on this section...
+lookups are constant time, so the total time complexity is going to
+be bounded by the number of entries in the table times the number of
+table lookups it takes to compute one entry in the table. Later we may
+be able to show not all of the table needs / will be computed lowering
+complexity.
+
+The size of the node table is trivial to upper bound. There are $2k+2$
+dimensions: the node's type (2 values), the node's block ($k$ values),
+$k$ dimensions for the number of nodes in each block that have gone
+before ($\le s_i + 1 | i=1..k$), and $k$ dimensions for the number of
+nodes in each block that have gone before and selected yes ($\le s_i +
+1 | i=1..k$). This leads to the following statement,
+\begin{align*}
+  NodeTableSize &= o\left( 2k \prod_{i=1}^k s_i+1 \prod_{i=1}^k s_i+1
+  \right) \\
+  &= o\left( k \prod_{i=1}^k s_i^2 \right)
+  \intertext{If we further assume that the size of $\ell \le k$ of
+    the blocks are order $n$ and the rest are constant size, then the
+    size of the table reduces to}
+  NodeTableSize &= o\left( kn^{2\ell} \right) \footnotemark
+  \intertext{Next we need to find the complexity of the computing one
+    entry in the node table in terms of other table lookups. Each
+    entry computation takes 2 calls to the sched oracle, and then does
+    computation of the expected number of Yeses which is order $k$,
+    making the total complexity for the node table given the sched
+    table}
+  NodeTableSize &= o\left( k^2 \prod_{i=1}^k s_i^2 \right) \\
+  NodeTableSize &= o\left( k^2 n^{2\ell} \right)
+  \intertext{The size of the scheduler table is also trivial to upper
+    bound. There are $2k$ dimensions similar to the node table. By
+    similar reasoning}
+  SchedTableSize &= o\left( \prod_{i=1}^k s_i+1 \prod_{i=1}^k s_i+1
+  \right) \\
+  &= o\left( \prod_{i=1}^k s_i^2 \right)
+  \intertext{If we make the same assumption about block sizes this
+    reduces to}
+  SchedTableSize &= o \left( n^{2\ell} \right)
+  \intertext{The complexity for each entry in the scheduler table is
+    linear in $k$, because it makes $2k$ lookups to the node
+    table. Therefore the total complexity for constructing the
+    scheduler table is bounded by}
+  SchedTableSize &= o\left( k \prod_{i=1}^k s_i^2 \right) \\
+  SchedTableSize &= o \left( k n^{2\ell} \right)
+  \intertext{This leaves us with final time complexity of}
+  RunningTime &= o\left( k^2 \prod_{i=1}^k s_i^2 \right) \\
+  &= o\left( k^2 n^{2\ell} \right)
+\end{align*}
+\footnotetext{Note, this may be smaller $o\left( \ell n^{2\ell}
+  \right)$, not sure}
+
+Similarly the node table is the large of the two tables, and has space
+complexity equal to time complexity.
 

### 2012-12-03 block_dp.py
small change to default depth

@@ -301,7 +301,7 @@ class StrategicBlockCascadeSolver:
         for k,v in self.nc.iteritems():
             print k,v
 
-    def writeOnlineScheduleTree(self, filename, depth=5, prune=True, merge=False):
+    def writeOnlineScheduleTree(self, filename, depth=0, prune=True, merge=False):
         """
         Writes a tree of the optimal decisions for the scheduler
 
@@ -316,7 +316,7 @@ class StrategicBlockCascadeSolver:
                    .pdf extension, or most programs probably won't
                    recognize it
         depth    = Optional. The maximum depth the tree will descend to.
-                   Defaults to 5.
+                   Defaults to 0 (full depth).
         prune    = Optional. Whether or not to prune subtrees strategic
                    node will never choose. Defaults to True.
         merge    = Optional. Whether or not to merge subtrees with

### 2012-12-05 block_dp.py
Added myopic strategy (maybe buggy?) and function to calculate expected Ys

@@ -74,7 +74,7 @@ class StrategicBlockCascadeSolver:
     # choose
     """
 
-    def __init__(self, p, pi, blockSizes, blockAdjacency):
+    def __init__(self, p, pi, blockSizes, blockAdjacency, myopic=False):
         """
         Create Solver Object
 
@@ -88,6 +88,8 @@ class StrategicBlockCascadeSolver:
         blockAdjacency = block adjacency matrix (BxB double tuple) This
                          can be asymetric and contain any non negative
                          weights
+
+        myopic         = whether agents update myopically or strategically
         """
         self.p  = p
         self.pi = pi
@@ -96,6 +98,7 @@ class StrategicBlockCascadeSolver:
         self.B  = len(blockSizes)
         self.nc = {} # DP table for optimal node choices
         self.bc = {} # DP table for optimal scheduler block choices
+        self.myopic = myopic
 
         assert p >= 0 and p <= 0.5, "p must be between 0 and 0.5"
         assert pi > 0, "pi must be greater than 0"
@@ -153,62 +156,98 @@ class StrategicBlockCascadeSolver:
         # <<< TODO >>>
         #
         # This is not the right check! It should check that
-        # specifically ns_b is one less than self.bs_b
+        # specifically ns_b is one less than self.bs_b but these
+        # should be equivelent under standard operation.
         if sum(ns) == sum(self.bs) - 1:
             # Recursive edge case. There are no nodes to pick after
             # this, so it just performs a myopic decision.
 
-            # <<< TODO >>>
-            # Figure out if this is correct. Right now it doesn't
-            # factor its own decision into its objective. The purpose
-            # of this is to remove self loops when there is a nonzero
-            # diagonal term. This might not accomplish this, and may
-            # make this calculation innacurate.
+            # No
+            _ns = list(ns)
+            _ns[b] += 1
+            _ns = tuple(_ns)
             un = sum(a*(n - y) for a,y,n in zip(self.ba[b], ys,
-                ns)) + (self.pi if not t else 0)
-            uy = sum(a*y for a,y in zip(self.ba[b], ys)) + (self.pi
+                _ns)) + (self.pi if not t else 0)
+
+            # Yes
+            _ys = list(ys)
+            _ys[b] += 1
+            _ys = tuple(_ys)
+            uy = sum(a*y for a,y in zip(self.ba[b], _ys)) + (self.pi
                 if t else 0)
 
             # Choose Y when...
             choice = uy > un
[…]

### 2012-12-07 proposal.tex
Added files for proposal to help with paper

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Proposal: Studying strategic cascades using 2-blockmodels}
\author{T. Martin \& E. Brinkman}
\date{\today}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{fullpage} %my stuff was already two pages at standard margins

\begin{document}

\maketitle

\section{Introduction}
\label{intro}

The study of network games is a relatively new and very active area of research. It has become both more important and more applicable since the internet has made large scale social interaction easier and more quantifiable. A common topic in network games is that of contagious or cascading processes, in which a number of agents start with some property they then spread to their neighbors under some spreading rules. This model naturally represents phenomena such as the spreading of trends, technologies, or influence through people or groups, or cascading failures in structures such as power grids or banks. Our proposed research is about theoretical models of spreading and cascading processes on networks.

Many models with simple spreading rules have been proposed \cite{Arthur89, Morris00, Watts02} to explain, for example, how breaking news spreads over the internet or how a new technology (such as the iPod) spreads in popularity. These spreading rules utually take one of two forms. The rules either govern a stochastic spreading process, or they assume that each node in the network is a strategic agent which makes a decision (e.g. to buy an iPod or to buy a Zune) and derives greater utility if his neighbors make the same decision. To the best of our knowledge, all current strategic agent models make a simplifying assumption that the agents are only myopically strategic \cite{Chierichetti12}: they make decisions at each round to maximize their utility at that point in the game. But, each agent's behavior can have profound impact on the future state of the network and thus the agent's own final utility. Our interest is in studying network processes under the more realistic assumption that agents make decisions conscious of their future influence on outcomes, in order to maximize their expected final utility.

More specifically, we propose to research the impact of having strategic users: how much different are results if we assume users are strategic instead of myopic. To answer this question, we will use a model introduced in \cite{Chierichetti12} and described in Section~\ref{prob_statement}. Our contribution is to fully characterize the behavior of this model on a specific class of graphs, the 2-blockmodels, in hopes of learning more about the general case. Blockmodels have been studied extensively in the past \cite{Wang87, Snijders97} as a natural framing of networks in which we can think of a node having a type which influences its characteristics. For example, a blockmodel describing a social network could have types for each grade, and students with each type are more likely to connect to their own grade, and unlikely to connect to grades very far away.

\section{Problem Statement}
\label{prob_statement}
We propose studying a simple cascade model over an arbitrary social network. In this model each agent is represented by a node in a graph and all of their friends / neighbors are represented by edges in the same graph. Over the course of the game each agent will make an irreversible choice between one of two types ($Y$ or $N$) -- where agents that prefer $Y$ are less frequent -- and will get a payoff at the end of the game corresponding to the number of neighbors that chose the same type as well as a bonus if they chose their prefered type. Thus each agent is torn between choosing their prefered type and choosing the type that a majority of their neighbors chose. The game is played with a single node making a choice between types at each point in time. We are looking to choose an order or schedule over agents to maximize the number of minority ($Y$) choices. We are interested in two different classes of schedules, offline and online. Offline schedules must schedule the entire set of agents before the game is played, whereas online schedules can be revised as agents make their decisions. We are interested in the difference between the optimal number of minority types chosen when the agents behave myopically, meaning their choice optimizes their current payoff, and when the agents behave strategically, meaning their choice optimizes their expected payoff at the end of the game. Strategic agents vary significantly depending on how much information they have. Here we assume they know the entire graph structure, every other agents strategy, the probability of an agent’s type, all decided node's choices, and the schedule.

Formally the model is specified for a graph $G(V,E)$ where each agent is a node $v_i \in V, i={1..n}$. At every point in time $t={0..n}$ each agent is in one of three states, Yes, No, or Undecided ($v_{it} \in \{Y, N, U\}$). At time zero each agent starts off Undecided, then at each point in time one agent according to the schedule switches from Undecided to either Yes or No. The schedule is an ordered permutation ($\mathcal P$) of the nodes. For the offline schedule this is static a permutation chosen ahead of time, but in the online schedule the $j^{th}$ element of the permutation is a function of the graph after the previous time. If the permutation is definied as an $n$ vector of ${1..n}$  then $\mathcal P_t = f_{\mathcal M}(V_t)$ where $\mathcal P_t$ is the $t^{th}$ element of the permutation, $f_{\mathcal M}$ is an arbitrary function that specifies which node to choose next based off of the current graph and the model parameters $\mathcal M$, and $V_t$ is the state of the agents at time $t$. The optimal schedule is the schedule that maximizes $J = \sum_{i=1}^n \mathbb E[\mathbb I(v_{in} = Y)]$ with respect to the schedule $\mathcal P$, where $\mathbb I$ is the indicator function and $v_{it}$ is the state of agent $i$ at time $t$. Before the game is played each agent also gets a prefered type which is drawn from a bionmial where $p(type_i = Y) = p < \frac{1}{2}$. The utility of a node $i$ at time $t$ is $u_{it}(v_{it}) = \pi \mathbb I(v_{it} = type_i) + \sum_{j \in \mathcal N(i)} \mathbb I(v_{it} = v_{jt}), v_{it} \in \{Y, N\}$, where $\pi$ is a constant that determines how much utility an agent gets from choosing its prefered type. If an agent is deciding its type at time $t$ a myopic agent $i$ will choose to maxmimize its current utility $\arg\max_{v_{it} \in \{Y, N\}} u_{it}$ where as a strategic agent will choose to maximize its expected final utility $\arg\max_{v_{it} \in \{Y, N\}} \mathbb E[u_{in}]$. We are interested in looking at the difference between the optimal number of minority choosing agents when the agents are strategic versus myopic ($J_{myopic} / J_{strategic}$).

Ongoing work by Martin et al. suggests that the scheduler payoff is always lower in the strategic case than in the myopic case, but we are interested quantifying this difference. To tackle this problem we propose investigating efficient algorithms for finding the optimal scheduling strategies on specific classes of graphs, which we hope will provide insight into quantifying the difference between the expected number of agents picking the minority type when the agents are strategic versus myopic.

We believe that an efficient dynamic programming algorithm exists for finding the optimal schedule on graphs that can be specified as a $2$-block graph. We define a $k$-block graph as any graph whose adjacency matrix can be represented as symmetric block matrix with $k^2$ blocks such that each block is either all $1$'s or all $0$'s. The idea behind the algorithm is to do a pruned backward induction from potential termination states. Because agents in a single block are substitutable, the potential choice at each round is significantly reduced. This combined with pruning should provide the necessary requirements to make this algorithm efficient. Work by Chierichetti et al.\cite{Chierichetti12} has already bounded the optimal schedule payout for arbitrary graphs, however applying an algorithm similar to ours for strategic agents should be no worse in complexity for myopic agents. In addition to the optimal offline schedule, the inductive nature of this algorithm should mean it also calculates the optimal online schedule. This efficient optimal algorithm should allow us to calculate the difference between strategic and myopic agents under offline and online schedules, and will hopefully give insight into bounds on the difference for arbitrary 2-block graphs.

There are a number of possible extensions for this algorithm that should also broaden the class of graphs that our results could apply to. These extensions include scaling to $k$-block graphs, directed graphs, and stochastic block graphs. Extending the algorithm to $k$-block graphs shouldn’t conceptually change the algorithm, but we believe that the original algorithm may scale exponentially in $k$ for a $k$-block graph. However, for bounded $k$, the complexity is still be moderately efficient. Additionally, scaling the algorithm up to $k$-blocks may expose room for improvement in the algorithm and provide further insight into quantifying the difference between myopic and strategic agents in this setting. Modifying the algorithm to account for directed graphs as long as they still fit into a blockmodel is also likely trivial and would further increase the number of graphs that we can analyze theoretically although the applicability of directed graphs is not immediately apparent. Another potentially easy extension of this would be to look at stochastic blockmodels\cite{Wang87, Snijders97}. It seems reasonable that the algorithm for static block graph models might extend in expectation to unrealized (and hence offline scheduled) stochastic blockmodels. This extension could likely never extend to realized graphs or to online schedules, but stochastic blockmodels are much closer to graphs found experimentally than $k$-block graphs.

\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2012-12-07 clique_dp.py
We don't need this

@@ -1,304 +1,0 @@
-from decimal import *
-import sys
-
-'''
-  General outline:
-    This code has a nested dictionary, answers, which is the table containing all values. It takes four arguments, in order:
-      # people who have already chosen Y
-      # people who have already chosen N
-      # people left to choose
-      a string defining which value we are interested in:
-        'yes-count': the number of Y-decisions I expect to be made, at the end, given this situation:
-                     answers[100][0][1]['yes-count'] = 101
-        'no-count': see above
-        'yes-decision': the choice a Y-type would make in this situation. Output is one of the constants Y, N:
-                        answers[100][0][1]['yes-decision'] = Y
-        'no-decision': see above
-        'yes-yes-value': the utility a yes-type would get for choosing yes, in this situation.
-                         answers[100][0][1]['yes-yes-value'] = 100 + pi
-        'yes-no-value': see above
-        'no-yes-value': see above
-        'no-no-value': see above
-    The values of the dictionary are computed when they are first referenced, using the appropriately named methods below.
-    Some values are preset, such as the axes of the table and some constants
-
-  We represent numbers using the Decimal class to avoid weird behavior from rounding errors
-
-'''
-
-# the range we are interested in (should be odd, x axis range). for display purposes only.
-# gives the maximum |#Y - #N| we are concerned about.
-a = 13
-
-# how many rounds we look at (network size, or y axis range)
-b = 70
-
-#No need to change these
-c = (a-1)/2 # the midpoint of x-range, used because we start with that many Y decisions
-Y = 0 # a constant representing the choice Y
-N = 20 # a constant representing the choice N
-dim = b+20 # the size of our answers table
-
-# contains all relevant values
-answers = {}
-
-#####################################################
-
-'''
-  The next methods are used to compute values in answers, or return value if
-  it has already been computed. These are the real meat of the program
-'''
-def yes_count(yes, no, n, p, pi):
[…]

### 2012-12-08 star_colorplots.py
Added code to make colorplots for the star

@@ -1,0 +1,40 @@
+import matplotlib.pyplot as plt
+from block_dp import StrategicBlockCascadeSolver
+from numpy import arange, zeros
+from pylab import *
+
+def p_vs_pi(p, pi):
+    return StrategicBlockCascadeSolver(p, pi, (1, 10), ((0,1),(1,0))).expectedYs() / \
+           StrategicBlockCascadeSolver(p, pi, (1, 10), ((0,1),(1,0)), True).expectedYs()
+
+
+def p_vs_n(p, n):
+    return StrategicBlockCascadeSolver(p, .9, (1, n), ((0,1),(1,0))).expectedYs() / \
+           StrategicBlockCascadeSolver(p, .9, (1, n), ((0,1),(1,0)), True).expectedYs()
+
+def pi_vs_n(pi, n):
+    return StrategicBlockCascadeSolver(.45, pi, (1, n), ((0,1),(1,0))).expectedYs() / \
+           StrategicBlockCascadeSolver(.45, pi, (1, n), ((0,1),(1,0)), True).expectedYs()
+
+
+def do_plotting(xlist,ylist, Z, x_start, x_inc, y_start, y_inc, dim, xlabel, ylabel):
+    X,Y = meshgrid(xlist, ylist)
+    plt.pcolor(X, Y, Z, vmax=abs(Z).max(), vmin=0)
+    plt.axis([x_start, x_start + x_inc*float(dim-1), y_start, y_start + y_inc*float(dim-1)])
+    plt.xlabel(xlabel)
+    plt.ylabel(ylabel)
+    plt.colorbar()
+    plt.show()
+
+def x_vs_y(x_start, x_inc, y_start, y_inc, dim, func, x_label, y_label):
+    x_list = arange(x_start, x_start + x_inc * float(dim), x_inc)
+    y_list = arange(y_start, y_start + y_inc * float(dim), y_inc)
+    Z = zeros((dim, dim))
+    for i in range(dim):
+        for j in range(dim):
+            Z[j, i] = func(x_list[i], y_list[j])
+    do_plotting(x_list, y_list, Z, x_start, x_inc, y_start, y_inc, dim, x_label, y_label)
+
+x_vs_y(.1, .01, .2, .025, 30, p_vs_pi, 'p', 'pi')
+x_vs_y(.1, .01, 1, 1, 30, p_vs_n, 'p', 'n')
+x_vs_y(.2, .025, 1, 1, 30, pi_vs_n, 'pi', 'n')

### 2012-12-08 star_colorplots.py
40 is a better parameter. Takes longer but looks better.

@@ -35,6 +35,6 @@ def x_vs_y(x_start, x_inc, y_start, y_inc, dim, func, x_label, y_label):
             Z[j, i] = func(x_list[i], y_list[j])
     do_plotting(x_list, y_list, Z, x_start, x_inc, y_start, y_inc, dim, x_label, y_label)
 
-x_vs_y(.1, .01, .2, .025, 30, p_vs_pi, 'p', 'pi')
-x_vs_y(.1, .01, 1, 1, 30, p_vs_n, 'p', 'n')
-x_vs_y(.2, .025, 1, 1, 30, pi_vs_n, 'pi', 'n')
+x_vs_y(.1, .01, .2, .025, 40, p_vs_pi, 'p', 'pi')
+x_vs_y(.1, .01, 1, 1, 40, p_vs_n, 'p', 'n')
+x_vs_y(.2, .025, 1, 1, 40, pi_vs_n, 'pi', 'n')

### 2012-12-09 paper.tex
Removed pdfs from .gitignore Added bibtex files to .gitignore Added clique parameter plots Added clique and grant plot scripts Moved proposal into paper Added motes to paper about potential sections Changed name of write_up.tex to paper.tex

--- 2012-12-07 proposal.tex
@@
 \documentclass{article}
-\usepackage[utf8]{inputenc}
-
-\title{Proposal: Studying strategic cascades using 2-blockmodels}
-\author{T. Martin \& E. Brinkman}
-\date{\today}
 
@@
 \usepackage{amsfonts}
-\usepackage{fullpage} %my stuff was already two pages at standard margins
+\usepackage{amsmath}
+\usepackage{amssymb}
+
+\title{Cascades, Product Conversion, Whatever}
+\author{T. Martian \& E. Brinkbot}
 
@@
 
-The study of network games is a relatively new and very active area of research.
-It has become both more important and more applicable since the internet has made large scale social interaction easier and more quantifiable.
-A common topic in network games is that of contagious or cascading processes, in which a number of agents start with some property they then spread to their neighbors under some spreading rules.
-This model naturally represents phenomena such as the spreading of trends, technologies, or influence through people or groups, or cascading failures in structures such as power grids or banks.
-Our proposed research is about theoretical models of spreading and cascading processes on networks.
+The study of network games is a relatively new and very active area of
+research. It has become both more important and more applicable since
+the internet has made large scale social interaction easier and more
+quantifiable. A common topic in network games is that of contagious or
+cascading processes, in which a number of agents start with some
+property they then spread to their neighbors under some spreading
+rules. This model naturally represents phenomena such as the spreading
+of trends, technologies, or influence through people or groups, or
+cascading failures in structures such as power grids or banks. Our
+proposed research is about theoretical models of spreading and
+cascading processes on networks.
 
-Many models with simple spreading rules have been proposed \cite{Arthur89, Morris00, Watts02} to explain, for example, how breaking news spreads over the internet or how a new technology (such as the iPod) spreads in popularity.
-These spreading rules utually take one of two forms.
-The rules either govern a stochastic spreading process, or they assume that each node in the network is a strategic agent which makes a decision (e.g.
-to buy an iPod or to buy a Zune) and derives greater utility if his neighbors make the same decision.
-To the best of our knowledge, all current strategic agent models make a simplifying assumption that the agents are only myopically strategic \cite{Chierichetti12}: they make decisions at each round to maximize their utility at that point in the game.
-But, each agent's behavior can have profound impact on the future state of the network and thus the agent's own final utility.
-Our interest is in studying network processes under the more realistic assumption that agents make decisions conscious of their future influence on outcomes, in order to maximize their expected final utility.
+Many models with simple spreading rules have been proposed
+\cite{Arthur89, Morris00, Watts02} to explain, for example, how
+breaking news spreads over the internet or how a new technology (such
+as the iPod) spreads in popularity. These spreading rules utually take
+one of two forms. The rules either govern a stochastic spreading
+process, or they assume that each node in the network is a strategic
+agent which makes a decision (e.g. to buy an iPod or to buy a Zune)
+and derives greater utility if his neighbors make the same
+decision. To the best of our knowledge, all current strategic agent
+models make a simplifying assumption that the agents are only
+myopically strategic \cite{Chierichetti12}: they make decisions at
+each round to maximize their utility at that point in the game. But,
+each agent's behavior can have profound impact on the future state of
+the network and thus the agent's own final utility. Our interest is in
+studying network processes under the more realistic assumption that
+agents make decisions conscious of their future influence on outcomes,
+in order to maximize their expected final utility.
 
-More specifically, we propose to research the impact of having strategic users: how much different are results if we assume users are strategic instead of myopic.
-To answer this question, we will use a model introduced in \cite{Chierichetti12} and described in Section~\ref{prob_statement}.
-Our contribution is to fully characterize the behavior of this model on a specific class of graphs, the 2-blockmodels, in hopes of learning more about the general case.
-Blockmodels have been studied extensively in the past \cite{Wang87, Snijders97} as a natural framing of networks in which we can think of a node having a type which influences its characteristics.
-For example, a blockmodel describing a social network could have types for each grade, and students with each type are more likely to connect to their own grade, and unlikely to connect to grades very far away.
+More specifically, we propose to research the impact of having
+strategic users: how much different are results if we assume users are
+strategic instead of myopic. To answer this question, we will use a
+model introduced in \cite{Chierichetti12} and described in
+Section~\ref{prob_statement}. Our contribution is to fully
+characterize the behavior of this model on a specific class of graphs,
+the 2-blockmodels, in hopes of learning more about the general
+case. Blockmodels have been studied extensively in the past
+\cite{Wang87, Snijders97} as a natural framing of networks in which we
+can think of a node having a type which influences its
+characteristics. For example, a blockmodel describing a social network
+could have types for each grade, and students with each type are more
+likely to connect to their own grade, and unlikely to connect to
+grades very far away.
+
+\section{Previous Work???}
+
+Do we want to split up the introduction??
+Also, is it possible to show that finding the optimal equilibrium is
+NP-complete / PPAD-complete?
 
@@
 \label{prob_statement}
-We propose studying a simple cascade model over an arbitrary social network.
-In this model each agent is represented by a node in a graph and all of their friends / neighbors are represented by edges in the same graph.
-Over the course of the game each agent will make an irreversible choice between one of two types ($Y$ or $N$) -- where agents that prefer $Y$ are less frequent -- and will get a payoff at the end of the game corresponding to the number of neighbors that chose the same type as well as a bonus if they chose their prefered type.
-Thus each agent is torn between choosing their prefered type and choosing the type that a majority of their neighbors chose.
-The game is played with a single node making a choice between types at each point in time.
-We are looking to choose an order or schedule over agents to maximize the number of minority ($Y$) choices.
-We are interested in two different classes of schedules, offline and online.
-Offline schedules must schedule the entire set of agents before the game is played, whereas online schedules can be revised as agents make their decisions.
-We are interested in the difference between the optimal number of minority types chosen when the agents behave myopically, meaning their choice optimizes their current payoff, and when the agents behave strategically, meaning their choice optimizes their expected payoff at the end of the game.
-Strategic agents vary significantly depending on how much information they have.
-Here we assume they know the entire graph structure, every other agents strategy, the probability of an agent’s type, all decided node's choices, and the schedule.
+We propose studying a simple cascade model over an arbitrary social
+network. In this model each agent is represented by a node in a graph
+and all of their friends / neighbors are represented by edges in the
+same graph. Over the course of the game each agent will make an
+irreversible choice between one of two types ($Y$ or $N$) -- where
+agents that prefer $Y$ are less frequent -- and will get a payoff at
+the end of the game corresponding to the number of neighbors that
+chose the same type as well as a bonus if they chose their prefered
+type. Thus each agent is torn between choosing their prefered type and
+choosing the type that a majority of their neighbors chose. The game
+is played with a single node making a choice between types at each
+point in time. We are looking to choose an order or schedule over
+agents to maximize the number of minority ($Y$) choices. We are
+interested in two different classes of schedules, offline and
+online. Offline schedules must schedule the entire set of agents
+before the game is played, whereas online schedules can be revised as
+agents make their decisions. We are interested in the difference
+between the optimal number of minority types chosen when the agents
+behave myopically, meaning their choice optimizes their current
+payoff, and when the agents behave strategically, meaning their choice
+optimizes their expected payoff at the end of the game. Strategic
+agents vary significantly depending on how much information they
+have. Here we assume they know the entire graph structure, every other
+agents strategy, the probability of an agent’s type, all decided
+node's choices, and the schedule.
 
-Formally the model is specified for a graph $G(V,E)$ where each agent is a node $v_i \in V, i={1..n}$.
-At every point in time $t={0..n}$ each agent is in one of three states, Yes, No, or Undecided ($v_{it} \in \{Y, N, U\}$).
-At time zero each agent starts off Undecided, then at each point in time one agent according to the schedule switches from Undecided to either Yes or No.
-The schedule is an ordered permutation ($\mathcal P$) of the nodes.
-For the offline schedule this is static a permutation chosen ahead of time, but in the online schedule the $j^{th}$ element of the permutation is a function of the graph after the previous time.
-If the permutation is definied as an $n$ vector of ${1..n}$  then $\mathcal P_t = f_{\mathcal M}(V_t)$ where $\mathcal P_t$ is the $t^{th}$ element of the permutation, $f_{\mathcal M}$ is an arbitrary function that specifies which node to choose next based off of the current graph and the model parameters $\mathcal M$, and $V_t$ is the state of the agents at time $t$.
-The optimal schedule is the schedule that maximizes $J = \sum_{i=1}^n \mathbb E[\mathbb I(v_{in} = Y)]$ with respect to the schedule $\mathcal P$, where $\mathbb I$ is the indicator function and $v_{it}$ is the state of agent $i$ at time $t$.
-Before the game is played each agent also gets a prefered type which is drawn from a bionmial where $p(type_i = Y) = p < \frac{1}{2}$.
-The utility of a node $i$ at time $t$ is $u_{it}(v_{it}) = \pi \mathbb I(v_{it} = type_i) + \sum_{j \in \mathcal N(i)} \mathbb I(v_{it} = v_{jt}), v_{it} \in \{Y, N\}$, where $\pi$ is a constant that determines how much utility an agent gets from choosing its prefered type.
-If an agent is deciding its type at time $t$ a myopic agent $i$ will choose to maxmimize its current utility $\arg\max_{v_{it} \in \{Y, N\}} u_{it}$ where as a strategic agent will choose to maximize its expected final utility $\arg\max_{v_{it} \in \{Y, N\}} \mathbb E[u_{in}]$.
-We are interested in looking at the difference between the optimal number of minority choosing agents when the agents are strategic versus myopic ($J_{myopic} / J_{strategic}$).
+Formally the model is specified for a graph $G(V,E)$ where each agent
+is a node $v_i \in V, i={1..n}$. At every point in time $t={0..n}$
+each agent is in one of three states, Yes, No, or Undecided ($v_{it}
+\in \{Y, N, U\}$). At time zero each agent starts off Undecided, then
+at each point in time one agent according to the schedule switches
+from Undecided to either Yes or No. The schedule is an ordered
+permutation ($\mathcal P$) of the nodes. For the offline schedule this
+is static a permutation chosen ahead of time, but in the online
+schedule the $j^{th}$ element of the permutation is a function of the
+graph after the previous time. If the permutation is definied as an
+$n$ vector of ${1..n}$ then $\mathcal P_t = f_{\mathcal M}(V_t)$ where
+$\mathcal P_t$ is the $t^{th}$ element of the permutation,
+$f_{\mathcal M}$ is an arbitrary function that specifies which node to
+choose next based off of the current graph and the model parameters
+$\mathcal M$, and $V_t$ is the state of the agents at time $t$. The
+optimal schedule is the schedule that maximizes $J = \sum_{i=1}^n
+\mathbb E[\mathbb I(v_{in} = Y)]$ with respect to the schedule
+$\mathcal P$, where $\mathbb I$ is the indicator function and $v_{it}$
+is the state of agent $i$ at time $t$. Before the game is played each
+agent also gets a prefered type which is drawn from a bionmial where
+$p(type_i = Y) = p < \frac{1}{2}$. The utility of a node $i$ at time
+$t$ is $u_{it}(v_{it}) = \pi \mathbb I(v_{it} = type_i) + \sum_{j \in
+  \mathcal N(i)} \mathbb I(v_{it} = v_{jt}), v_{it} \in \{Y, N\}$,
+where $\pi$ is a constant that determines how much utility an agent
+gets from choosing its prefered type. If an agent is deciding its type
+at time $t$ a myopic agent $i$ will choose to maxmimize its current
+utility $\arg\max_{v_{it} \in \{Y, N\}} u_{it}$ where as a strategic
+agent will choose to maximize its expected final utility
+$\arg\max_{v_{it} \in \{Y, N\}} \mathbb E[u_{in}]$. We are interested
+in looking at the difference between the optimal number of minority
+choosing agents when the agents are strategic versus myopic
+($J_{myopic} / J_{strategic}$).
 
-Ongoing work by Martin et al.
-suggests that the scheduler payoff is always lower in the strategic case than in the myopic case, but we are interested quantifying this difference.
-To tackle this problem we propose investigating efficient algorithms for finding the optimal scheduling strategies on specific classes of graphs, which we hope will provide insight into quantifying the difference between the expected number of agents picking the minority type when the agents are strategic versus myopic.
+Ongoing work by Martin et al. suggests that the scheduler payoff is
+always lower in the strategic case than in the myopic case, but we are
+interested quantifying this difference. To tackle this problem we
+propose investigating efficient algorithms for finding the optimal
+scheduling strategies on specific classes of graphs, which we hope
+will provide insight into quantifying the difference between the
+expected number of agents picking the minority type when the agents
+are strategic versus myopic.
 
-We believe that an efficient dynamic programming algorithm exists for finding the optimal schedule on graphs that can be specified as a $2$-block graph.
-We define a $k$-block graph as any graph whose adjacency matrix can be represented as symmetric block matrix with $k^2$ blocks such that each block is either all $1$'s or all $0$'s.
-The idea behind the algorithm is to do a pruned backward induction from potential termination states.
-Because agents in a single block are substitutable, the potential choice at each round is significantly reduced.
-This combined with pruning should provide the necessary requirements to make this algorithm efficient.
-Work by Chierichetti et al.\cite{Chierichetti12} has already bounded the optimal schedule payout for arbitrary graphs, however applying an algorithm similar to ours for strategic agents should be no worse in complexity for myopic agents.
-In addition to the optimal offline schedule, the inductive nature of this algorithm should mean it also calculates the optimal online schedule.
-This efficient optimal algorithm should allow us to calculate the difference between strategic and myopic agents under offline and online schedules, and will hopefully give insight into bounds on the difference for arbitrary 2-block graphs.
+We believe that an efficient dynamic programming algorithm exists for
+finding the optimal schedule on graphs that can be specified as a
+$2$-block graph. We define a $k$-block graph as any graph whose
+adjacency matrix can be represented as symmetric block matrix with
+$k^2$ blocks such that each block is either all $1$'s or all
+$0$'s. The idea behind the algorithm is to do a pruned backward
+induction from potential termination states. Because agents in a
+single block are substitutable, the potential choice at each round is
+significantly reduced. This combined with pruning should provide the
+necessary requirements to make this algorithm efficient. Work by
+Chierichetti et al.\cite{Chierichetti12} has already bounded the
+optimal schedule payout for arbitrary graphs, however applying an
+algorithm similar to ours for strategic agents should be no worse in
+complexity for myopic agents. In addition to the optimal offline
+schedule, the inductive nature of this algorithm should mean it also
+calculates the optimal online schedule. This efficient optimal
+algorithm should allow us to calculate the difference between
+strategic and myopic agents under offline and online schedules, and
+will hopefully give insight into bounds on the difference for
+arbitrary 2-block graphs.
 
-There are a number of possible extensions for this algorithm that should also broaden the class of graphs that our results could apply to.
-These extensions include scaling to $k$-block graphs, directed graphs, and stochastic block graphs.
-Extending the algorithm to $k$-block graphs shouldn’t conceptually change the algorithm, but we believe that the original algorithm may scale exponentially in $k$ for a $k$-block graph.
-However, for bounded $k$, the complexity is still be moderately efficient.
-Additionally, scaling the algorithm up to $k$-blocks may expose room for improvement in the algorithm and provide further insight into quantifying the difference between myopic and strategic agents in this setting.
-Modifying the algorithm to account for directed graphs as long as they still fit into a blockmodel is also likely trivial and would further increase the number of graphs that we can analyze theoretically although the applicability of directed graphs is not immediately apparent.
-Another potentially easy extension of this would be to look at stochastic blockmodels\cite{Wang87, Snijders97}.
-It seems reasonable that the algorithm for static block graph models might extend in expectation to unrealized (and hence offline scheduled) stochastic blockmodels.
-This extension could likely never extend to realized graphs or to online schedules, but stochastic blockmodels are much closer to graphs found experimentally than $k$-block graphs.
+There are a number of possible extensions for this algorithm that
+should also broaden the class of graphs that our results could apply
+to. These extensions include scaling to $k$-block graphs, directed
+graphs, and stochastic block graphs. Extending the algorithm to
+$k$-block graphs shouldn’t conceptually change the algorithm, but we
+believe that the original algorithm may scale exponentially in $k$ for
+a $k$-block graph. However, for bounded $k$, the complexity is still
+be moderately efficient. Additionally, scaling the algorithm up to
+$k$-blocks may expose room for improvement in the algorithm and
+provide further insight into quantifying the difference between myopic
+and strategic agents in this setting. Modifying the algorithm to
+account for directed graphs as long as they still fit into a
+blockmodel is also likely trivial and would further increase the
+number of graphs that we can analyze theoretically although the
+applicability of directed graphs is not immediately apparent. Another
+potentially easy extension of this would be to look at stochastic
+blockmodels\cite{Wang87, Snijders97}. It seems reasonable that the
+algorithm for static block graph models might extend in expectation to
+unrealized (and hence offline scheduled) stochastic blockmodels. This
+extension could likely never extend to realized graphs or to online
+schedules, but stochastic blockmodels are much closer to graphs found
+experimentally than $k$-block graphs.
+
+\section{Model}
+
+Model Description goes here... This probably should steal a lot of
+problem statement. My thoughts are this should define the game
+
+\subsection{Block Models}
+
+Then maybe a subsection specifically about block models
+
+\begin{align*}
+  & k && \text{Number of blocks} \\
+  & \{s_i\}_{i=1..k} && \text{Number of nodes in each block}
+\end{align*}
+
+\section{Algorithm}
+
+The algorithm uses two lookup tables (one for the scheduler, and one
+for the nodes) to determine the optimal play given the relevant
+statistics of the game at decision time. Each table has a dimension
+for every relevant play statistic for the deciding agent, and contains
+their optimal choice as well as the expected number of Yeses in each
+block after that choice is made (which is necessary for callers to
+decide on their optimal decision, as expected payoffs are only a
+function of the expected number of Yeses at the end).
+
+These two tables back two oracles (wrong terminology?) which will
+return a precomputed value if it's already in the table, or they'll
+compute it as defined below. This can lead to a recursive cascade of
+computation, which is bounded by the size of the tables times the time
+to compute each element in terms of a lookup in one of them.
+
+We'll call the scheduler oracle
+\begin{align*}
+  & \operatorname{sched}(\{c_i\}, \{y_i\})
+  \intertext{and the node oracle}
+  & \operatorname{node}(t, b, \{c_i\}, \{y_i\})
+  \intertext{where}
+  & type && \text{Node's type (Yes or No)} \\
+  & n && \text{Node block} \\
+  & \{c_i\} && \text{Number of already chosen nodes by block} \\
+  & \{y_i\} && \text{Number of Yes chosen nodes by block}
+\end{align*}
+We can show (we need to show) that that's all of the relevant
+statistics either agent needs to know to determine a unique optimal
+decision.
+
+The scheduler just needs to check each possible choice of next block,
+and for each block calculate the expected number of Yeses by weighting
+the expected number of Yeses for a Yes or No node by the probability
+of a Yes or No node. This involves at most $2k$ calls to the node
+oracle, and is sufficient for determining the optimal choice of the
+scheduler.
+
+The nodes just have to find their expected value if they choose Yes or
+choose No. This is just comparing two calls to the sched oracle.
+
+Combining these two yields a polynomial in $n$ time algorithm for
+solving arbitrary block models.
+
+\section{Complexity}
+
+lookups are constant time, so the total time complexity is going to
+be bounded by the number of entries in the table times the number of
+table lookups it takes to compute one entry in the table. Later we may
+be able to show not all of the table needs / will be computed lowering
+complexity.
+
+The size of the node table is trivial to upper bound. There are $2k+2$
+dimensions: the node's type (2 values), the node's block ($k$ values),
+$k$ dimensions for the number of nodes in each block that have gone
+before ($\le s_i + 1 | i=1..k$), and $k$ dimensions for the number of
+nodes in each block that have gone before and selected yes ($\le s_i +
+1 | i=1..k$). This leads to the following statement,
+\begin{align*}
+  NodeTableSize &= o\left( 2k \prod_{i=1}^k s_i+1 \prod_{i=1}^k s_i+1
+  \right) \\
+  &= o\left( k \prod_{i=1}^k s_i^2 \right)
+  \intertext{If we further assume that the size of $\ell \le k$ of
+    the blocks are order $n$ and the rest are constant size, then the
+    size of the table reduces to}
+  NodeTableSize &= o\left( kn^{2\ell} \right) \footnotemark
+  \intertext{Next we need to find the complexity of the computing one
+    entry in the node table in terms of other table lookups. Each
+    entry computation takes 2 calls to the sched oracle, and then does
+    computation of the expected number of Yeses which is order $k$,
+    making the total complexity for the node table given the sched
+    table}
+  NodeTableSize &= o\left( k^2 \prod_{i=1}^k s_i^2 \right) \\
+  NodeTableSize &= o\left( k^2 n^{2\ell} \right)
+  \intertext{The size of the scheduler table is also trivial to upper
+    bound. There are $2k$ dimensions similar to the node table. By
+    similar reasoning}
+  SchedTableSize &= o\left( \prod_{i=1}^k s_i+1 \prod_{i=1}^k s_i+1
+  \right) \\
+  &= o\left( \prod_{i=1}^k s_i^2 \right)
+  \intertext{If we make the same assumption about block sizes this
+    reduces to}
+  SchedTableSize &= o \left( n^{2\ell} \right)
+  \intertext{The complexity for each entry in the scheduler table is
+    linear in $k$, because it makes $2k$ lookups to the node
+    table. Therefore the total complexity for constructing the
+    scheduler table is bounded by}
+  SchedTableSize &= o\left( k \prod_{i=1}^k s_i^2 \right) \\
+  SchedTableSize &= o \left( k n^{2\ell} \right)
+  \intertext{This leaves us with final time complexity of}
+  RunningTime &= o\left( k^2 \prod_{i=1}^k s_i^2 \right) \\
+  &= o\left( k^2 n^{2\ell} \right)
+\end{align*}
+\footnotetext{Note, this may be smaller $o\left( \ell n^{2\ell}
+  \right)$, not sure}
+
+Similarly the node table is the large of the two tables, and has space
+complexity equal to time complexity.
+
+\section{Results?}
+
+Dunno if this is the best title for this section. Basically this is
+where we look at the graphs and maybe show some timing things?
+
+\section{Discussion and Future Work}
+
+Talk about the significance, patterns, stuff like that that? Talk
+about future work in quantifying for general graphs, although it may
+not be possible?? At least in some nice form.
 
@@
 \bibliography{references}
+
 \end{document}

### 2012-12-09 block_dp.py

@@ -101,7 +101,7 @@ class StrategicBlockCascadeSolver:
         self.myopic = myopic
 
         assert p >= 0 and p <= 0.5, "p must be between 0 and 0.5"
-        assert pi > 0, "pi must be greater than 0"
+        assert pi >= 0, "pi must be greater than or equal to 0"
         assert len(self.ba) == self.B, "BlockAdjacency must be BxB"
         assert all(len(row) == self.B for row in self.ba), "BlockAdjacency must be BxB"
         assert type(self.bs) is tuple, "BlockSizes must be a tuple"

### 2012-12-09 clique_plots.py

@@ -1,0 +1,56 @@
+import matplotlib.pyplot as plt
+import numpy as np
+from block_dp import StrategicBlockCascadeSolver
+
+def makePlot(values, ext, name, xaxis='', yaxis=''):
+    ny, nx = values.shape
+    xoff = float(ext[1] - ext[0])/(nx - 1)/2
+    yoff = float(ext[3] - ext[2])/(ny - 1)/2
+    ext = (ext[0]-xoff, ext[1]+xoff, ext[2]-yoff, ext[3]+yoff)
+
+    f = plt.figure()
+    ax = f.gca()
+    p = ax.imshow(values, extent=ext, aspect='auto', origin='lower',
+                  interpolation='nearest')
+    cb = f.colorbar(p)
+    ax.grid()
+    ax.set_xlabel(xaxis, fontsize=18)
+    ax.set_ylabel(yaxis, fontsize=18)
+    f.savefig(name + '.pdf')
+    print 'Created ' + name + '.pdf'
+
+def getStrat(p, pi, n):
+    return StrategicBlockCascadeSolver(p, pi, (n,), ((1,),)).expectedYs()
+
+def getMyop(p, pi, n):
+    return StrategicBlockCascadeSolver(p, pi, (n,), ((1,),), True).expectedYs()
+
+getStratV = np.vectorize(getStrat)
+getMyopV  = np.vectorize(getMyop)
+
+pr  = (0.01, 0.5)
+pir = (0.01, 10)
+p = np.linspace(pr[0],   pr[1],  40)
+pi = np.linspace(pir[0], pir[1], 40)
+P, PI = np.meshgrid(p, pi)
+
+ratio = getStratV(P,PI,10) / getMyopV(P,PI,10)
+makePlot(ratio, pr + pir, 'clique_n10', 'p', 'pi')
+
+pir = (0.01, 5)
+nr  = (1,15)
+n  = np.linspace(nr[0],   nr[1],  15)
+pi = np.linspace(pir[0], pir[1], 40)
+N, PI = np.meshgrid(n, pi)
+
+ratio = getStratV(0.25,PI,N) / getMyopV(0.25,PI,N)
+makePlot(ratio, nr + pir, 'clique_p0.25', 'n', 'pi')
+
+pr = (0.01, 0.5)
+nr  = (1,15)
+n  = np.linspace(nr[0],   nr[1],  15)
[…]

### 2012-12-09 grant_plots.py

@@ -1,0 +1,57 @@
+import matplotlib.pyplot as plt
+import numpy as np
+from block_dp import StrategicBlockCascadeSolver
+
+def makePlot(values, ext, name, xaxis='', yaxis=''):
+    ny, nx = values.shape
+    xoff = float(ext[1] - ext[0])/(nx - 1)/2
+    yoff = float(ext[3] - ext[2])/(ny - 1)/2
+    ext = (ext[0]-xoff, ext[1]+xoff, ext[2]-yoff, ext[3]+yoff)
+
+    f = plt.figure()
+    ax = f.gca()
+    p = ax.imshow(values, extent=ext, aspect='auto', origin='lower',
+                  interpolation='nearest')
+    cb = f.colorbar(p)
+    ax.grid()
+    ax.set_xlabel(xaxis, fontsize=18)
+    ax.set_ylabel(yaxis, fontsize=18)
+    f.savefig(name + '.pdf')
+    print 'Created ' + name + '.pdf'
+
+# CHANGE
+def getStrat(p, pi, n):
+    return StrategicBlockCascadeSolver(p, pi, (n,), ((1,),)).expectedYs()
+
+# CHANGE
+def getMyop(p, pi, n):
+    return StrategicBlockCascadeSolver(p, pi, (n,), ((1,),), True).expectedYs()
+
+getStratV = np.vectorize(getStrat)
+getMyopV  = np.vectorize(getMyop)
+
+pr  = (0.01, 0.5)
+pir = (0.01, 10)
+p = np.linspace(pr[0],   pr[1],  40)
+pi = np.linspace(pir[0], pir[1], 40)
+P, PI = np.meshgrid(p, pi)
+
+ratio = getStratV(P,PI,10) / getMyopV(P,PI,10)
+makePlot(ratio, pr + pir, 'grant_n10', 'p', 'pi')
+
+nr  = (1,15)
+n  = np.linspace(nr[0],   nr[1],  15)
+pi = np.linspace(pir[0], pir[1], 40)
+N, PI = np.meshgrid(n, pi)
+
+ratio = getStratV(0.25,PI,N) / getMyopV(0.25,PI,N)
+makePlot(ratio, nr + pir, 'grant_p0.25', 'n', 'pi')
+
+pr = (0.01, 0.5)
+nr  = (1,15)
+n  = np.linspace(nr[0],   nr[1],  15)
[…]

### 2012-12-10 grant_plots.py
Fixed grant_plot

@@ -20,32 +20,42 @@ def makePlot(values, ext, name, xaxis='', yaxis=''):
     print 'Created ' + name + '.pdf'
 
 # CHANGE
-def getStrat(p, pi, n):
-    return StrategicBlockCascadeSolver(p, pi, (n,), ((1,),)).expectedYs()
+def getStrat(p, pi, n, r):
+    m = n-3
+    a = int(round(m*r))
+    b = m-a
+    return StrategicBlockCascadeSolver(p, pi, (1,a,1,b,1),
+        ((0,1,0,0,0),(1,0,1,0,0),(0,1,0,1,0),(0,0,1,0,1),(0,0,0,1,0))
+        ).expectedYs()
 
 # CHANGE
-def getMyop(p, pi, n):
-    return StrategicBlockCascadeSolver(p, pi, (n,), ((1,),), True).expectedYs()
+def getMyop(p, pi, n, r):
+    m = n-3
+    a = int(round(m*r))
+    b = m-a
+    return StrategicBlockCascadeSolver(p, pi, (1,a,1,b,1),
+        ((0,1,0,0,0),(1,0,1,0,0),(0,1,0,1,0),(0,0,1,0,1),(0,0,0,1,0)),
+        True).expectedYs()
 
 getStratV = np.vectorize(getStrat)
 getMyopV  = np.vectorize(getMyop)
 
 pr  = (0.01, 0.5)
 pir = (0.01, 10)
-p = np.linspace(pr[0],   pr[1],  40)
-pi = np.linspace(pir[0], pir[1], 40)
+p = np.linspace(pr[0],   pr[1],  10)
+pi = np.linspace(pir[0], pir[1], 10)
 P, PI = np.meshgrid(p, pi)
 
-ratio = getStratV(P,PI,10) / getMyopV(P,PI,10)
-makePlot(ratio, pr + pir, 'grant_n10', 'p', 'pi')
+ratio = getStratV(P,PI,12,0.5) / getMyopV(P,PI,12,0.5)
+makePlot(ratio, pr + pir, 'grant_n12_r0.5', 'p', 'pi')
 
 nr  = (1,15)
 n  = np.linspace(nr[0],   nr[1],  15)
 pi = np.linspace(pir[0], pir[1], 40)
 N, PI = np.meshgrid(n, pi)
 
[…]

### 2012-12-10 star_plots.py
Added timing code, adjusted star colorbar

@@ -1,0 +1,49 @@
+import matplotlib.pyplot as plt
+import time
+from block_dp import StrategicBlockCascadeSolver
+from numpy import arange, zeros
+from pylab import *
+
+STAR_ADJ = ((0,1),(1,0))
+
+def p_vs_pi(p, pi):
+    return StrategicBlockCascadeSolver(p, pi, (1, 10), STAR_ADJ).expectedYs() / \
+           StrategicBlockCascadeSolver(p, pi, (1, 10), STAR_ADJ, True).expectedYs()
+
+
+def p_vs_n(p, n):
+    return StrategicBlockCascadeSolver(p, .9, (1, n), STAR_ADJ).expectedYs() / \
+           StrategicBlockCascadeSolver(p, .9, (1, n), STAR_ADJ, True).expectedYs()
+
+def pi_vs_n(pi, n):
+    return StrategicBlockCascadeSolver(.45, pi, (1, n), STAR_ADJ).expectedYs() / \
+           StrategicBlockCascadeSolver(.45, pi, (1, n), STAR_ADJ, True).expectedYs()
+
+
+def do_plotting(xlist,ylist, Z, x_start, x_inc, y_start, y_inc, dim, xlabel, ylabel, name):
+    X,Y = meshgrid(xlist, ylist)
+    f = plt.figure()
+    ax = f.gca()
+    #ax.grid()
+    plt.pcolor(X, Y, Z, vmax=abs(Z).max(), vmin=abs(Z).min())
+    plt.axis([x_start, x_start + x_inc*float(dim-1), y_start,
+              y_start + y_inc*float(dim-1)])
+    plt.xlabel(xlabel, fontsize=18)
+    plt.ylabel(ylabel, fontsize=18)
+    plt.colorbar()
+    f.savefig(name + '.pdf')
+
+def x_vs_y(x_start, x_inc, y_start, y_inc, dim, func, x_label, y_label, name):
+    x_list = arange(x_start, x_start + x_inc * float(dim), x_inc)
+    y_list = arange(y_start, y_start + y_inc * float(dim), y_inc)
+    Z = zeros((dim, dim))
+    for i in range(dim):
+        for j in range(dim):
+            Z[j, i] = func(x_list[i], y_list[j])
+    do_plotting(x_list, y_list, Z, x_start, x_inc, 
[…]

### 2012-12-10 timings.py

@@ -1,0 +1,21 @@
+import matplotlib.pyplot as plt
+import time
+from block_dp import StrategicBlockCascadeSolver
+from numpy import zeros
+
+def calc_timings(p, pi, n_start, n_end, iterations):
+    total_timings = zeros(n_end-n_start)
+    for i in range(iterations):
+        timings = zeros(n_end-n_start)
+        for n in range(n_start, n_end):
+            start = time.clock()
+            StrategicBlockCascadeSolver(p,pi,(1,n),STAR_ADJ).expectedYs()
+            end = time.clock()
+            timings[n-n_start] = end-start
+        total_timings += timings
+    total_timings = total_timings/iterations
+    plt.plot(total_timings)
+    plt.xlabel('n', fontsize=18)
+    plt.ylabel('time (s)', fontsize=18)
+    plt.show()
+    return total_timings

### 2012-12-11 paper.tex
Added results/discussion to paper, a couple files to compute graphs
Results/discussion are preliminary. Need a bit about cloud graphs and
some spellchecking.

Most graph-computing files are hodgepodge but I haven't had time to
clean them up.

@@
 \usepackage{amssymb}
+\usepackage{caption}
+\usepackage{subcaption}
+
+\captionsetup[subfigure]{labelformat=empty}
 
@@
 
-\section{Results?}
+\section{Results \& Discussion}
+We implemented our dynamic program algorithm and ran it on several categories of graphs in order to guide intuition for theoretical work regarding this problem.
+Our primary concern was the difference in expected number of Yes decisions for the optimal adaptive schedule given strategic or myopic users.
+We aim to characterize situations under which strategic users give more Yes decisions than myopic users, or vice versa.
+Our secondary concern was testing the predicted complexity of our algorithms.
 
-Dunno if this is the best title for this section. Basically this is
-where we look at the graphs and maybe show some timing things?
+We test a star graph, a clique, and a special graph we call a cloud graph.
+A cloud graph consists of two singular vertices of degree one, one singular vertex of degree two, and two clouds of many vertices, each of degree two.
+Each of the singular degree one vertices is connected to every node in a distinct cloud.
+The singular degree two vertex is connected to every node in both clouds.
+This graph, under certain parameters, provably obtains more $Y$ adoptions for strategic users.
 
-\section{Discussion and Future Work}
+We examine the ratio of expected number of $Y$s between strategic and myopic while varying the parameters $p, \pi, n$.
+Colorplots of the ratio for the set value $n=10$ but varying $p, pi$ can be found in Figure~\ref{fig:ratio}.
+The primary lesson we learned from Figure~\ref{fig:ratio} is that the behavior on these graphs is extremely complex.
+There appears is no clear general characterization of how the ratio will behave.
+
+Though these plots provide little obvious insight into the general case of graphs, we can extract valuable information about specific behaviors and provide some upper and lower bounds on the extremes of the ratio.
+
+The ratio is increasing in $p$ for the star graph but decreasing in $p$ for the clique.
+Even more strangely, the ratio is (mostly) increasing in $\pi$ for the star graph but depends on the $p$ value for the clique.
+We see markedly different behavior when $\pi = 1$.
+This is the point at which agents are indifferent between choosing their own type and going with the expected majority.
+This indifference is unique to $\pi=1$, and our tie breaking methods lead to significant differences in outcome.
+
+We learn several things regarding the question of whether strategic agents can ever give more Y adoptions than myopic agents.
+Data for the star graph supports the theoretical result, that myopic is always better on the (and thus the ratio is bounded by 1).
+The clique plot suggests an interesting result.
+For small $p, \pi$, strategic is better than myopic.
+This is an unexpected, but reasonable result.
+For $\pi=1+\epsilon$, only 1 Y decision is required to start a Y cascade with strategic users, but 2 Y decisions are required with myopic users.
+So the ratio can be as large as $\frac{1}{p}$.
+We also confirm some cascade proofs we've had for the clique and cloud graphs, namely that we can achieve either a $Y$ or an $N$ cascade on the cloud graph, depending on the parameters, and that for many parameters the clique achieves an $N$ cascade.
+
+We leave out plots which vary $n$, in the interest of space. These plots give similarly varied results.
+
+Careful analysis of plots in Figure~\ref{fig:ratio} reveals that our graphs have sharp bands of color, in which small changes in $p$ or $\pi$ result in drastic changes in ratio.
+We graph numerical values in Figure~\ref{fig:ratio2} in order to investigate this phenomenon on the star graph.
+Drastic ratio changes correspond to changes in fundamental behavior of strategic nodes on the star.
+For example, as $p$ or $pi$ get larger, the situations under which a strategic $Y$ type edge node might choose $N$ change.
+For low enough $\pi$ (on the star graph), $Y$ type nodes will choose $N$ after only one edge node has chosen $N$.
+As $\pi$ rises, this stubbornness threshold also rises in discrete jumps as seen on the graph.
+
+Lastly, we investigate the computational complexity of our algorithm in Figure~\ref{fig:time} by measuring computation time over varied graph sizes.
+We time the star graph, which has one block that scales with $n$, and the cloud graph, which has two blocks that scale with $n$.
+As predicted, running time is quadratic for the star graph and quartic for the cloud graph.
+
+\begin{figure}
+        \centering
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{star_n10.pdf}
+                \caption{Star}
+        \end{subfigure}
+        ~ 
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{clique_n10.pdf}
+                \caption{Clique}
+        \end{subfigure}
+        ~ 
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{grant_n10.pdf}
+                \caption{Cloud}
+        \end{subfigure}
+        \caption{Ratio of strategic:myopic Y adoptions for varying $p, \pi$.}
+        \label{fig:ratio}
+\end{figure}
+
+\begin{figure}
+        \centering
+        \begin{subfigure}[b]{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{{p_ratio_pi0.9n20}.pdf}
+                \caption{Varying p}
+        \end{subfigure}
+        ~ 
+        \begin{subfigure}[b]{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{{pi_ratio_p0.45n20}.pdf}
+                \caption{Varying pi}
+        \end{subfigure}
+        \caption{Ratio of strategic:myopic Y adoptions for varying $p, \pi$ on star graph.}
+        \label{fig:ratio2}
+\end{figure}
+
+\begin{figure}
+        \centering
+        \begin{subfigure}[b]{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{star_time.pdf}
+                \caption{Star}
+        \end{subfigure}
+        ~ 
+        \begin{subfigure}[b]{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{cloud_time.pdf}
+                \caption{Cloud}
+        \end{subfigure}
+        \caption{Code runtime for varying graph size. Blue line is best quadratic fit, green line is best quartic fit.}
+        \label{fig:time}
+\end{figure}
+
+\section{Future Work}
 

### 2012-12-11 timings.py

@@ -1,11 +1,40 @@
 import matplotlib.pyplot as plt
 import time
 from block_dp import StrategicBlockCascadeSolver
-from numpy import zeros
+from numpy import arange, zeros
 
-def calc_timings(p, pi, n_start, n_end, iterations):
+STAR_ADJ = ((0,1),(1,0))
+GRANT_ADJ = ((0,1,0,0,0),(1,0,1,0,0),(0,1,0,1,0),(0,0,1,0,1),(0,0,0,1,0))
+
+def calc_p_ratios_star(pi, n, prange):
+    timings = []
+    for p in prange:
+        ratio = StrategicBlockCascadeSolver(p,pi,(1,n),STAR_ADJ).expectedYs() / \
+        float(StrategicBlockCascadeSolver(p,pi,(1,n),STAR_ADJ, True).expectedYs())
+        timings.append(ratio)
+    #plt.plot(prange, timings, 'o')
+    #plt.xlabel('p', fontsize=18)
+    #plt.ylabel('ratio', fontsize=18)
+    #plt.show()
+    return timings
+
+def calc_pi_ratios_star(p, n, pirange):
+    timings = []
+    for pi in pirange:
+        ratio = StrategicBlockCascadeSolver(p,pi,(1,n),STAR_ADJ).expectedYs() / \
+        float(StrategicBlockCascadeSolver(p,pi,(1,n),STAR_ADJ, True).expectedYs())
+        timings.append(ratio)
+    #plt.plot(pirange, timings, 'o')
+    #plt.xlabel('pi', fontsize=18)
+    #plt.ylabel('ratio', fontsize=18)
+    #plt.show()
+    return timings
+
+def calc_timings_star(p, pi, n_start, n_end, iterations):
     total_timings = zeros(n_end-n_start)
     for i in range(iterations):
+        if i%2 == 0:
+            continue
         timings = zeros(n_end-n_start)
         for n in range(n_start, n_end):
             start = time.clock()
@@ -19,3 +48,79 @@ def calc_timings(p, pi, n_start, n_end, iterations):
     plt.ylabel('time (s)', fontsize=18)
     plt.show()
     return total_timings
+
+def getStratGrant(p, pi, n, r):
+    m = n-3
+    a = int(round(m*r))
+    b = m-a
+    return StrategicBlockCascadeSolver(p, pi, (1,a,1,b,1),
[…]

### 2012-12-11 paper.tex
Updated paper for algorithm and complexity section. Added some 'cloud' / grant graphs

--- 2012-12-09 paper.tex
@@
 \section{Algorithm}
+\label{sec:algorithm}
 
@@
 for the nodes) to determine the optimal play given the relevant
-statistics of the game at decision time. Each table has a dimension
-for every relevant play statistic for the deciding agent, and contains
-their optimal choice as well as the expected number of Yeses in each
-block after that choice is made (which is necessary for callers to
-decide on their optimal decision, as expected payoffs are only a
-function of the expected number of Yeses at the end).
+statistics of the game at every decision time. Each table has a
+dimension for every relevant play statistic for the deciding agent,
+and contains their optimal choice as well as the expected number of
+Yeses in each block after that choice is made (which is necessary for
+callers to decide on their optimal decision, as expected payoffs are
+only a function of the expected number of Yeses at the end of the
+game).
 
-These two tables back two oracles (wrong terminology?) which will
-return a precomputed value if it's already in the table, or they'll
-compute it as defined below. This can lead to a recursive cascade of
-computation, which is bounded by the size of the tables times the time
-to compute each element in terms of a lookup in one of them.
+The two tables recursively reference each other to calculate their
+entries, where each entry is the choice, and the expected number of
+Yesses at the end of the game in each block conditioned on that
+choice. If an entry is already calculated, then the lookup is constant
+time, otherwise the lookup may cause a cascade of calculations, which
+is bounded by the polynomial time to compute both tables.\footnote{It
+  is possible that instead of looking these up on the fly, he table
+  could be precomputed to speed up the complexity slightly, but we
+  believe that this speedup would be very slight, and would make the
+  algorithm much more complicated}
 
-We'll call the scheduler oracle
+We will represent the tables as recursive functions, with the implicit
+understanding that we're caching results to get a polynomial time
+algorithm.
+
+To determine the optimal block choice for the scheduler, the decision
+function only needs to know, ho many nodes from each block have
+already gone, and what proportion (or number) of the nodes have chosen
+Yes. Because nodes within a block are exchangeable, this information
+completely characterizes the state of the game at the time of
+scheduler choice.
+
+Similarly, to determine the optimal choice (Yes or No) of a node, the
+node only needs (has available) its own type, what block it is in, the
+number of nodes in each block that have already chosen, and the number
+of those nodes that have chosen Yes.
+
+We formally define the optimal scheduler choice function as
 \begin{align*}
   & \operatorname{sched}(\{c_i\}, \{y_i\})
-  \intertext{and the node oracle}
+  \intertext{and the optimal node choice function as}
   & \operatorname{node}(t, b, \{c_i\}, \{y_i\})
   \intertext{where}
-  & type && \text{Node's type (Yes or No)} \\
+  & t && \text{Node's type (Yes or No)} \\
   & n && \text{Node block} \\
@@
 \end{align*}
-We can show (we need to show) that that's all of the relevant
-statistics either agent needs to know to determine a unique optimal
-decision.
 
-The scheduler just needs to check each possible choice of next block,
-and for each block calculate the expected number of Yeses by weighting
-the expected number of Yeses for a Yes or No node by the probability
-of a Yes or No node. This involves at most $2k$ calls to the node
-oracle, and is sufficient for determining the optimal choice of the
-scheduler.
+The scheduler needs to check the possible outcome given it picks a Yes
+or a No type node from each of the $k$ blocks that have a most one
+node possible to pick. It then marginalizes out the type of the node
+to calculate the expected number of Yesses for each choice of
+block. The optimal choice is simply the one that maximizes the
+expected number of Yesses.
 
-The nodes just have to find their expected value if they choose Yes or
-choose No. This is just comparing two calls to the sched oracle.
+A node needs to check its own expected final utility given it chooses
+Yes or No, and choose the choice that maximizes it. The node can query
+the scheduler function to determine the expected number of Yesses in
+each block conditioned on the node choosing Yes or No. The node then
+trivially calculates its expected utility for each choice, and picks
+the maximum.
 
-Combining these two yields a polynomial in $n$ time algorithm for
-solving arbitrary block models.
+Completely calculating the results of these functions is trivially
+simple, and in doing so completely finds the optimal online schedule
+and optimal node choice along that schedule.
 
@@
 
-lookups are constant time, so the total time complexity is going to
+See Section \ref{sec:algorithm} for an explanation of the algorithm.
+
+Lookups are constant time, so the total time complexity is going to
 be bounded by the number of entries in the table times the number of
-table lookups it takes to compute one entry in the table. Later we may
-be able to show not all of the table needs / will be computed lowering
-complexity.
+table lookups it takes to compute one entry in the table.
 
@@
   &= o\left( k \prod_{i=1}^k s_i^2 \right)
-  \intertext{If we further assume that the size of $\ell \le k$ of
-    the blocks are order $n$ and the rest are constant size, then the
+  \intertext{If we further assume that $\ell \le k$ of
+    the blocks are size order $n$ and the rest are constant size, then the
     size of the table reduces to}
-  NodeTableSize &= o\left( kn^{2\ell} \right) \footnotemark
-  \intertext{Next we need to find the complexity of the computing one
-    entry in the node table in terms of other table lookups. Each
-    entry computation takes 2 calls to the sched oracle, and then does
+  NodeTableSize &= o\left( kn^{2\ell} \right)
+  \intertext{Each node table entry
+    computation takes 2 calls to the sched function, and then does
     computation of the expected number of Yeses which is order $k$,
@@
     table}
-  NodeTableSize &= o\left( k^2 \prod_{i=1}^k s_i^2 \right) \\
-  NodeTableSize &= o\left( k^2 n^{2\ell} \right)
+  NodeTableComplexity &= o\left( k^2 \prod_{i=1}^k s_i^2 \right) \\
+  NodeTableComplexity &= o\left( k^2 n^{2\ell} \right)
   \intertext{The size of the scheduler table is also trivial to upper
@@
     scheduler table is bounded by}
-  SchedTableSize &= o\left( k \prod_{i=1}^k s_i^2 \right) \\
-  SchedTableSize &= o \left( k n^{2\ell} \right)
+  SchedTableComplexity &= o\left( k \prod_{i=1}^k s_i^2 \right) \\
+  SchedTableComplexity &= o \left( k n^{2\ell} \right)
   \intertext{This leaves us with final time complexity of}
@@
 \end{align*}
-\footnotetext{Note, this may be smaller $o\left( \ell n^{2\ell}
-  \right)$, not sure}
 
-Similarly the node table is the large of the two tables, and has space
+Similarly the node table is the larger of the two tables, and has space
 complexity equal to time complexity.

### 2012-12-11 grant_plots.py

@@ -41,15 +41,16 @@ getStratV = np.vectorize(getStrat)
 getMyopV  = np.vectorize(getMyop)
 
 pr  = (0.01, 0.5)
-pir = (0.01, 10)
-p = np.linspace(pr[0],   pr[1],  10)
-pi = np.linspace(pir[0], pir[1], 10)
+pir = (0.01, 2)
+p = np.linspace(pr[0],   pr[1],  20)
+pi = np.linspace(pir[0], pir[1], 20)
 P, PI = np.meshgrid(p, pi)
 
-ratio = getStratV(P,PI,12,0.5) / getMyopV(P,PI,12,0.5)
-makePlot(ratio, pr + pir, 'grant_n12_r0.5', 'p', 'pi')
+ratio = np.log(getStratV(P,PI,12,0.5) / getMyopV(P,PI,12,0.5))
+makePlot(ratio, pr + pir, 'cloud_n12_r0.5', 'p', 'pi')
 
 nr  = (1,15)
+pir = (0.01, 2)
 n  = np.linspace(nr[0],   nr[1],  15)
 pi = np.linspace(pir[0], pir[1], 40)
 N, PI = np.meshgrid(n, pi)

### 2012-12-11 paper.tex
Updated figure of "cloud" graph
Revised introduction, results & discussion

@@
 breaking news spreads over the internet or how a new technology (such
-as the iPod) spreads in popularity. These spreading rules utually take
+as the iPod) spreads in popularity. These spreading rules usually take
 one of two forms. The rules either govern a stochastic spreading
@@
 
-\section{Previous Work???}
-
-Do we want to split up the introduction??
-Also, is it possible to show that finding the optimal equilibrium is
-NP-complete / PPAD-complete?
+The analysis of strategic behavior on networks is not a new concept. Kearns et. al.
+introduced a convenient method for expressing games of this sort with their seminal
+work on graphical games \cite{Kearns01}. But, to the extent of our knowledge,
+nobody has attempted to characterize full graphical game models for cascade spreading.
+This is what we to below.
 
@@
 We aim to characterize situations under which strategic users give more Yes decisions than myopic users, or vice versa.
-Our secondary concern was testing the predicted complexity of our algorithms.
+Our secondary concern was testing the predicted computational complexity of our algorithms.
 
@@
 We examine the ratio of expected number of $Y$s between strategic and myopic while varying the parameters $p, \pi, n$.
-Colorplots of the ratio for the set value $n=10$ but varying $p, pi$ can be found in Figure~\ref{fig:ratio}.
+Colorplots of the ratio for the set value $n=10$ but varying $p, \pi$ can be found in Figure~\ref{fig:ratio}.
 The primary lesson we learned from Figure~\ref{fig:ratio} is that the behavior on these graphs is extremely complex.
-There appears is no clear general characterization of how the ratio will behave.
+There appears to be no clear general characterization of how the ratio will behave.
 
@@
 
-The ratio is increasing in $p$ for the star graph but decreasing in $p$ for the clique.
-Even more strangely, the ratio is (mostly) increasing in $\pi$ for the star graph but depends on the $p$ value for the clique.
+The ratio is increasing in $p$ for the star graph, decreasing in $p$ for the clique, and both (depending on $\pi$) for the cloud graph.
+Even more strangely, the ratio is (mostly) increasing in $\pi$ for the star graph but depends on the $p$ value for the clique and cloud graphs.
 We see markedly different behavior when $\pi = 1$.
 This is the point at which agents are indifferent between choosing their own type and going with the expected majority.
-This indifference is unique to $\pi=1$, and our tie breaking methods lead to significant differences in outcome.
+This indifference is unique to $\pi=1$, as our tie breaking methods lead to significant differences in outcome.
 
-We learn several things regarding the question of whether strategic agents can ever give more Y adoptions than myopic agents.
-Data for the star graph supports the theoretical result, that myopic is always better on the (and thus the ratio is bounded by 1).
+We learn several things regarding the question of whether strategic agents can ever give more $Y$ adoptions than myopic agents.
+Data for the star graph supports our theoretical result that myopic is always better on the star graph (and thus the ratio is bounded by 1).
 The clique plot suggests an interesting result.
 For small $p, \pi$, strategic is better than myopic.
-This is an unexpected, but reasonable result.
-For $\pi=1+\epsilon$, only 1 Y decision is required to start a Y cascade with strategic users, but 2 Y decisions are required with myopic users.
+This is an unexpected, but explainable result.
+For $\pi=1+\epsilon$, only 1 $Y$ decision is required to start a $ƒ$ cascade with strategic users, but 2 $Y$ decisions are required with myopic users.
 So the ratio can be as large as $\frac{1}{p}$.
@@
 
-We leave out plots which vary $n$, in the interest of space. These plots give similarly varied results.
+We leave out plots which vary $n$, in the interest of space, but these plots give similarly varied results.
 
-Careful analysis of plots in Figure~\ref{fig:ratio} reveals that our graphs have sharp bands of color, in which small changes in $p$ or $\pi$ result in drastic changes in ratio.
+Careful analysis of plots in Figure~\ref{fig:ratio} reveals that our graphs have sharp bands of color in which small changes in $p$ or $\pi$ result in drastic changes in ratio.
 We graph numerical values in Figure~\ref{fig:ratio2} in order to investigate this phenomenon on the star graph.
@@
                 \centering
-                \includegraphics[width=\textwidth]{grant_n10.pdf}
-                \caption{Cloud}
+                \includegraphics[width=\textwidth]{cloud_n10_r05_log.pdf}
+                \caption{Cloud\footnotemark}
         \end{subfigure}
@@
 \end{figure}
+\footnotetext{Log scale. White = $-\infty$ or $\log 0$}
 

### 2012-12-11 paper.tex
Cropped cloud_n10_r05_log.pdf to make diagram better
Added a few changes, really just premerge commit

--- 2012-12-11 paper.tex
@@
 \label{prob_statement}
+
 We propose studying a simple cascade model over an arbitrary social
@@
 
+Patterns may not exist, but there may still be order level
+relationships / bounds that are possible.
+
+See if we can prove the problem is PPAD or NP-complete.
+
 \bibliographystyle{plain}

### 2012-12-12 paper.tex

--- 2012-12-11 paper.tex
@@
 
-The analysis of strategic behavior on networks is not a new concept. Kearns et. al.
-introduced a convenient method for expressing games of this sort with their seminal
-work on graphical games \cite{Kearns01}. But, to the extent of our knowledge,
-nobody has attempted to characterize full graphical game models for cascade spreading.
-This is what we to below.
-
-\section{Problem Statement}
-\label{prob_statement}
-We propose studying a simple cascade model over an arbitrary social
-network. In this model each agent is represented by a node in a graph
-and all of their friends / neighbors are represented by edges in the
-same graph. Over the course of the game each agent will make an
-irreversible choice between one of two types ($Y$ or $N$) -- where
-agents that prefer $Y$ are less frequent -- and will get a payoff at
-the end of the game corresponding to the number of neighbors that
-chose the same type as well as a bonus if they chose their prefered
-type. Thus each agent is torn between choosing their prefered type and
-choosing the type that a majority of their neighbors chose. The game
-is played with a single node making a choice between types at each
-point in time. We are looking to choose an order or schedule over
-agents to maximize the number of minority ($Y$) choices. We are
-interested in two different classes of schedules, offline and
-online. Offline schedules must schedule the entire set of agents
-before the game is played, whereas online schedules can be revised as
-agents make their decisions. We are interested in the difference
-between the optimal number of minority types chosen when the agents
-behave myopically, meaning their choice optimizes their current
-payoff, and when the agents behave strategically, meaning their choice
-optimizes their expected payoff at the end of the game. Strategic
-agents vary significantly depending on how much information they
-have. Here we assume they know the entire graph structure, every other
-agents strategy, the probability of an agent’s type, all decided
-node's choices, and the schedule.
-
-Formally the model is specified for a graph $G(V,E)$ where each agent
-is a node $v_i \in V, i={1..n}$. At every point in time $t={0..n}$
-each agent is in one of three states, Yes, No, or Undecided ($v_{it}
-\in \{Y, N, U\}$). At time zero each agent starts off Undecided, then
-at each point in time one agent according to the schedule switches
-from Undecided to either Yes or No. The schedule is an ordered
-permutation ($\mathcal P$) of the nodes. For the offline schedule this
-is static a permutation chosen ahead of time, but in the online
-schedule the $j^{th}$ element of the permutation is a function of the
-graph after the previous time. If the permutation is definied as an
-$n$ vector of ${1..n}$ then $\mathcal P_t = f_{\mathcal M}(V_t)$ where
-$\mathcal P_t$ is the $t^{th}$ element of the permutation,
-$f_{\mathcal M}$ is an arbitrary function that specifies which node to
-choose next based off of the current graph and the model parameters
-$\mathcal M$, and $V_t$ is the state of the agents at time $t$. The
-optimal schedule is the schedule that maximizes $J = \sum_{i=1}^n
-\mathbb E[\mathbb I(v_{in} = Y)]$ with respect to the schedule
-$\mathcal P$, where $\mathbb I$ is the indicator function and $v_{it}$
-is the state of agent $i$ at time $t$. Before the game is played each
-agent also gets a prefered type which is drawn from a bionmial where
-$p(type_i = Y) = p < \frac{1}{2}$. The utility of a node $i$ at time
-$t$ is $u_{it}(v_{it}) = \pi \mathbb I(v_{it} = type_i) + \sum_{j \in
-  \mathcal N(i)} \mathbb I(v_{it} = v_{jt}), v_{it} \in \{Y, N\}$,
-where $\pi$ is a constant that determines how much utility an agent
-gets from choosing its prefered type. If an agent is deciding its type
-at time $t$ a myopic agent $i$ will choose to maxmimize its current
-utility $\arg\max_{v_{it} \in \{Y, N\}} u_{it}$ where as a strategic
-agent will choose to maximize its expected final utility
-$\arg\max_{v_{it} \in \{Y, N\}} \mathbb E[u_{in}]$. We are interested
-in looking at the difference between the optimal number of minority
-choosing agents when the agents are strategic versus myopic
-($J_{myopic} / J_{strategic}$).
-
-Ongoing work by Martin et al. suggests that the scheduler payoff is
-always lower in the strategic case than in the myopic case, but we are
-interested quantifying this difference. To tackle this problem we
-propose investigating efficient algorithms for finding the optimal
-scheduling strategies on specific classes of graphs, which we hope
-will provide insight into quantifying the difference between the
-expected number of agents picking the minority type when the agents
-are strategic versus myopic.
-
-We believe that an efficient dynamic programming algorithm exists for
-finding the optimal schedule on graphs that can be specified as a
-$2$-block graph. We define a $k$-block graph as any graph whose
-adjacency matrix can be represented as symmetric block matrix with
-$k^2$ blocks such that each block is either all $1$'s or all
-$0$'s. The idea behind the algorithm is to do a pruned backward
-induction from potential termination states. Because agents in a
-single block are substitutable, the potential choice at each round is
-significantly reduced. This combined with pruning should provide the
-necessary requirements to make this algorithm efficient. Work by
-Chierichetti et al.\cite{Chierichetti12} has already bounded the
-optimal schedule payout for arbitrary graphs, however applying an
-algorithm similar to ours for strategic agents should be no worse in
-complexity for myopic agents. In addition to the optimal offline
-schedule, the inductive nature of this algorithm should mean it also
-calculates the optimal online schedule. This efficient optimal
-algorithm should allow us to calculate the difference between
-strategic and myopic agents under offline and online schedules, and
-will hopefully give insight into bounds on the difference for
-arbitrary 2-block graphs.
-
-There are a number of possible extensions for this algorithm that
-should also broaden the class of graphs that our results could apply
-to. These extensions include scaling to $k$-block graphs, directed
-graphs, and stochastic block graphs. Extending the algorithm to
-$k$-block graphs shouldn’t conceptually change the algorithm, but we
-believe that the original algorithm may scale exponentially in $k$ for
-a $k$-block graph. However, for bounded $k$, the complexity is still
-be moderately efficient. Additionally, scaling the algorithm up to
-$k$-blocks may expose room for improvement in the algorithm and
-provide further insight into quantifying the difference between myopic
-and strategic agents in this setting. Modifying the algorithm to
-account for directed graphs as long as they still fit into a
-blockmodel is also likely trivial and would further increase the
-number of graphs that we can analyze theoretically although the
-applicability of directed graphs is not immediately apparent. Another
-potentially easy extension of this would be to look at stochastic
-blockmodels\cite{Wang87, Snijders97}. It seems reasonable that the
-algorithm for static block graph models might extend in expectation to
-unrealized (and hence offline scheduled) stochastic blockmodels. This
-extension could likely never extend to realized graphs or to online
-schedules, but stochastic blockmodels are much closer to graphs found
-experimentally than $k$-block graphs.
+The analysis of strategic behavior on networks is not a new
+concept. Kearns et. al.  introduced a convenient method for expressing
+games of this sort with their seminal work on graphical games
+\cite{Kearns01}. But, to the extent of our knowledge, nobody has
+attempted to characterize full graphical game models for cascade
+spreading.  This is what we do below.
 
 \section{Model}
+\label{prob_statement}
 
-Model Description goes here... This probably should steal a lot of
-problem statement. My thoughts are this should define the game
+We propose a cascade spreading model that borrows heavily from the
+scheduler mediated cascade process introduced in
+\cite{Chierichetti12}. In our model every node in an undirected graph
+is a risk neutral rational agent. Each node is also assigned a binary
+type which affects their utility, pulled from a binomial
+distribution. In this paper we call the types Yes ($Y$) and No
+($N$). There is an additional scheduler agent, which, at each round of
+the game picks one of the nodes in the graph. At that moment the
+chosen node chooses to commit to a choice (also Yes or No) and the
+agent is committed to that choice for the rest of the game. The game
+ends when all nodes have committed to a choice.
 
-\subsection{Block Models}
+We keep the same scheduler behavior as in the previous paper. The
+schedulers utility is based off of the number of nodes that choose Yes
+at the end of the game. We assume the scheduler can change its plan
+after it sees what a node chooses. We also assume it has full
+knowledge of the nodes strategies, as well as knowledge of the full
+graph, and any game parameters. The only aspect the scheduler does not
+know is the individual nodes types.
 
-Then maybe a subsection specifically about block models
+The nodes utility is the sum of all of their neighbors that match
+their choice plus some constant ($\pi$) if their choice matches their
+type. Strategic nodes make decisions to maximize their expected
+profit. We assume strategic nodes know the schedulers decision making
+(or utility function), the graph structure, and the probability that a
+node is assigned Yes type ($p$), but not any other nodes type. To keep
+the model interesting, we restrict $p < 0.5$. Similarly myopic nodes
+only try to maximize their current utility, ignoring any nodes that
+has not made a decision.
 
+We consider games where either all nodes in the graph are strategic or
+myopic, and want to see what graphs / game parameters contribute to
+significant differences between the expected number of Yesses when
+nodes are strategic versus myopic.
+
+We formally specify the model as follows
 \begin{align*}
-  & k && \text{Number of blocks} \\
-  & \{s_i\}_{i=1..k} && \text{Number of nodes in each block}
+  & G(V,E) && \text{social network} \\
+  & |V| = n \\
+  & c_i \in \{Y,N\} && \text{choice of node $i$} \\
+  & t_i \in \{Y, N\} && \text{type of node $i$} \\
+  & p(t_i = Y) = p < 0.5 \\
+  & u_i(\mathbf c) = \pi \mathbb I[t_i = c_i] + \sum_{j \in N(i)}
+  \mathbb I[c_j = c_i] && \text{node utility} \\
+  & sched(\mathbf c) && \text{schedule function}
 \end{align*}
+where $\mathbb I$ is the indicator function, and $N$ is the neighbor
+function. The schedule function returns the next node to pick given
+the choices that have been made so far.
+
+The full game can be described by the following algorithm. The
+scheduler picks an optimal first node in the graph. That node chooses
+either Yes or No based on all of the parameters and its
+knowledge. Based on this result the scheduler picks a new node, and so
+on until every node is chosen and the game finishes.
+
+Given this game, we are interested in quantifying
+\begin{equation*}
+  \frac{\mathbb E[\#Y|strategic]}{\mathbb E[\#Y|myopic]}.
+\end{equation*}
+
+Is seems likely that computing the strategic choices and payouts is a
+hard problem, but we will show an algorithm that can compute an
+optimal online schedule and calculate $\mathbb E[\#Y|stragetic]$ in
+polynomial time for arbitrary block models.
+
+A graph is a $k$-block model is the vertices can be divided into $k$
+disjoint subsets such that every node in the same subset has
+incoming and outgoing edges to the same set of nodes. Another way to
+view this property is by looking at the adjacency matrix of the
+graph. A block model graph can be written as a symmetric block matrix
+with $k^2$ blocks. For the sake of the algorithm, we will define
+\begin{equation*}
+  \{s_i\}_{i=1..k}
+\end{equation*}
+as the number of nodes in each block.
 
@@
 
-The algorithm uses two lookup tables (one for the scheduler, and one
+Our algorithm uses two lookup tables (one for the scheduler, and one
 for the nodes) to determine the optimal play given the relevant
@@
 
+Patterns may not exist, but there may still be order level
+relationships / bounds that are possible.
+
+See if we can prove the problem is PPAD or NP-complete.
+
+Offline scheduling
+
+There are a number of possible extensions for this algorithm that
+should also broaden the class of graphs that our results could apply
+to. These extensions include scaling to $k$-block graphs, directed
+graphs, and stochastic block graphs. Extending the algorithm to
+$k$-block graphs shouldn’t conceptually change the algorithm, but we
+believe that the original algorithm may scale exponentially in $k$ for
+a $k$-block graph. However, for bounded $k$, the complexity is still
+be moderately efficient. Additionally, scaling the algorithm up to
+$k$-blocks may expose room for improvement in the algorithm and
+provide further insight into quantifying the difference between myopic
+and strategic agents in this setting. Modifying the algorithm to
+account for directed graphs as long as they still fit into a
+blockmodel is also likely trivial and would further increase the
+number of graphs that we can analyze theoretically although the
+applicability of directed graphs is not immediately apparent. Another
+potentially easy extension of this would be to look at stochastic
+blockmodels\cite{Wang87, Snijders97}. It seems reasonable that the
+algorithm for static block graph models might extend in expectation to
+unrealized (and hence offline scheduled) stochastic blockmodels. This
+extension could likely never extend to realized graphs or to online
+schedules, but stochastic blockmodels are much closer to graphs found
+experimentally than $k$-block graphs.
+
 \bibliographystyle{plain}

### 2012-12-12 paper.tex
Finished future work, and corrected some stuff. Passed my initial test

@@
 \usepackage{natbib}
+\usepackage{array}
 \usepackage{graphicx}
@@
 ($N$). There is an additional scheduler agent, which, at each round of
-the game picks one of the nodes in the graph. At that moment the
-chosen node chooses to commit to a choice (also Yes or No) and the
-agent is committed to that choice for the rest of the game. The game
-ends when all nodes have committed to a choice.
+the game picks one of the nodes in the graph. The chosen node picks a
+``choice'' (also Yes or No) and the agent is committed to that
+``choice'' for the rest of the game. The game ends when all nodes have
+picked a ``choice.''
 
@@
 knowledge. Based on this result the scheduler picks a new node, and so
-on until every node is chosen and the game finishes.
+on until every node has been picked and the game finishes.
 
@@
 \begin{equation*}
-  \frac{\mathbb E[\#Y|strategic]}{\mathbb E[\#Y|myopic]}.
+  \frac{\mathbb E[\#Y|strategic]}{\mathbb E[\#Y|myopic]}
 \end{equation*}
+for a given family of graphs with different game parameters.
 
@@
 
-A graph is a $k$-block model is the vertices can be divided into $k$
+A graph is a $k$-block model if the vertices can be divided into $k$
 disjoint subsets such that every node in the same subset has
@@
 as the number of nodes in each block.
+
+An example of a 2-block model would be the star graph, which can be
+expressed in adjacency matrix form as
+\begin{equation*}
+  \begin{array}{r}
+    1 \{ \\
+    n-1 \{
+  \end{array}
+  \left[ \begin{array}{cc}
+      0 & 1 \\
+      1 & 0
+      \end{array} \right]
+\end{equation*}
+and has $\mathbf s = \{1, n-1\}$.
 
@@
   NodeTableComplexity &= o\left( k^2 \prod_{i=1}^k s_i^2 \right) \\
-  NodeTableComplexity &= o\left( k^2 n^{2\ell} \right)
+  &= o\left( k^2 n^{2\ell} \right)
   \intertext{The size of the scheduler table is also trivial to upper
@@
   SchedTableComplexity &= o\left( k \prod_{i=1}^k s_i^2 \right) \\
-  SchedTableComplexity &= o \left( k n^{2\ell} \right)
+  &= o \left( k n^{2\ell} \right)
   \intertext{This leaves us with final time complexity of}
@@
 \section{Results \& Discussion}
-We implemented our dynamic program algorithm and ran it on several categories of graphs in order to guide intuition for theoretical work regarding this problem.
-Our primary concern was the difference in expected number of Yes decisions for the optimal adaptive schedule given strategic or myopic users.
-We aim to characterize situations under which strategic users give more Yes decisions than myopic users, or vice versa.
-Our secondary concern was testing the predicted computational complexity of our algorithms.
+We implemented our dynamic program algorithm and ran it on several
+categories of graphs in order to guide intuition for theoretical work
+regarding this problem. Our primary concern was the difference in
+expected number of Yes decisions for the optimal adaptive schedule
+given strategic or myopic users. We aim to characterize situations
+under which strategic users give more Yes decisions than myopic users,
+or vice versa. Our secondary concern was testing the predicted
+computational complexity of our algorithms.
 
-We test a star graph, a clique, and a special graph we call a cloud graph.
-A cloud graph consists of two singular vertices of degree one, one singular vertex of degree two, and two clouds of many vertices, each of degree two.
-Each of the singular degree one vertices is connected to every node in a distinct cloud.
-The singular degree two vertex is connected to every node in both clouds.
-This graph, under certain parameters, provably obtains more $Y$ adoptions for strategic users.
+We test a star graph, a clique, and a special graph we call a cloud
+graph. A cloud graph consists of two singular ``outer'' vertices of
+degree $a$ and $b$ respectively, one singular ``inner'' vertex of
+degree $a+b$, and two clouds of size $a$ and $b$ respectively, with
+each vertex of degree two. Each of the ``outer'' vertices is connected
+to every node in a distinct cloud. The singular ``inner'' vertex is
+connected to every node in both clouds. This graph, under certain
+parameters, provably obtains more $Y$ adoptions for strategic users.
 
-We examine the ratio of expected number of $Y$s between strategic and myopic while varying the parameters $p, \pi, n$.
-Colorplots of the ratio for the set value $n=10$ but varying $p, \pi$ can be found in Figure~\ref{fig:ratio}.
-The primary lesson we learned from Figure~\ref{fig:ratio} is that the behavior on these graphs is extremely complex.
-There appears to be no clear general characterization of how the ratio will behave.
+We examine the ratio of expected number of $Y$s between strategic and
+myopic while varying the parameters $p, \pi, n$. Colorplots of the
+ratio for the set value $n=10$ but varying $p, \pi$ can be found in
+Figure~\ref{fig:ratio}. The primary lesson we learned from
+Figure~\ref{fig:ratio} is that the behavior on these graphs is
+extremely complex. There appears to be no clear general
+characterization of how the ratio will behave.
 
-Though these plots provide little obvious insight into the general case of graphs, we can extract valuable information about specific behaviors and provide some upper and lower bounds on the extremes of the ratio.
+Though these plots provide little obvious insight into the general
+case of graphs, we can extract valuable information about specific
+behaviors and provide some upper and lower bounds on the extremes of
+the ratio.
 
-The ratio is increasing in $p$ for the star graph, decreasing in $p$ for the clique, and both (depending on $\pi$) for the cloud graph.
-Even more strangely, the ratio is (mostly) increasing in $\pi$ for the star graph but depends on the $p$ value for the clique and cloud graphs.
-We see markedly different behavior when $\pi = 1$.
-This is the point at which agents are indifferent between choosing their own type and going with the expected majority.
-This indifference is unique to $\pi=1$, as our tie breaking methods lead to significant differences in outcome.
+The ratio is increasing in $p$ for the star graph, decreasing in $p$
+for the clique, and both (depending on $\pi$) for the cloud
+graph. Even more strangely, the ratio is (mostly) increasing in $\pi$
+for the star graph but depends on the $p$ value for the clique and
+cloud graphs. We see markedly different behavior when $\pi = 1$. This
+is the point at which agents are indifferent between choosing their
+own type and going with the expected majority. This indifference is
+unique to $\pi=1$, as our tie breaking methods lead to significant
+differences in outcome (nodes pick No in the event of a tie).
 
-We learn several things regarding the question of whether strategic agents can ever give more $Y$ adoptions than myopic agents.
-Data for the star graph supports our theoretical result that myopic is always better on the star graph (and thus the ratio is bounded by 1).
-The clique plot suggests an interesting result.
-For small $p, \pi$, strategic is better than myopic.
-This is an unexpected, but explainable result.
-For $\pi=1+\epsilon$, only 1 $Y$ decision is required to start a $ƒ$ cascade with strategic users, but 2 $Y$ decisions are required with myopic users.
-So the ratio can be as large as $\frac{1}{p}$.
-We also confirm some cascade proofs we've had for the clique and cloud graphs, namely that we can achieve either a $Y$ or an $N$ cascade on the cloud graph, depending on the parameters, and that for many parameters the clique achieves an $N$ cascade.
+We learn several things regarding the question of whether strategic
+agents can ever give more $Y$ adoptions than myopic agents. Data for
+the star graph supports our theoretical result that myopic is always
+better on the star graph (and thus the ratio is bounded by 1). The
+clique plot suggests an interesting result. For small $p, \pi$,
+strategic is better than myopic. This is an unexpected, but
+explainable result. For $\pi=1+\epsilon$, only 1 $Y$ decision is
+required to start a $Y$ cascade with strategic users, but 2 $Y$ decisions
+are required with myopic users. So the ratio can be as large as
+$\frac{1}{p}$. We also confirm some cascade proofs we've had for the
+clique and cloud graphs, namely that we can achieve either a $Y$ or an
+$N$ cascade on the cloud graph, depending on the parameters, and that
+for many parameters the clique achieves an $N$ cascade.
 
-We leave out plots which vary $n$, in the interest of space, but these plots give similarly varied results.
+We leave out plots which vary $n$, in the interest of space, but these
+plots give similarly varied results.
 
-Careful analysis of plots in Figure~\ref{fig:ratio} reveals that our graphs have sharp bands of color in which small changes in $p$ or $\pi$ result in drastic changes in ratio.
-We graph numerical values in Figure~\ref{fig:ratio2} in order to investigate this phenomenon on the star graph.
-Drastic ratio changes correspond to changes in fundamental behavior of strategic nodes on the star.
-For example, as $p$ or $pi$ get larger, the situations under which a strategic $Y$ type edge node might choose $N$ change.
-For low enough $\pi$ (on the star graph), $Y$ type nodes will choose $N$ after only one edge node has chosen $N$.
-As $\pi$ rises, this stubbornness threshold also rises in discrete jumps as seen on the graph.
+Careful analysis of plots in Figure~\ref{fig:ratio} reveals that our
+graphs have sharp bands of color in which small changes in $p$ or
+$\pi$ result in drastic changes in ratio. We graph numerical values in
+Figure~\ref{fig:ratio2} in order to investigate this phenomenon on the
+star graph. Drastic ratio changes correspond to changes in fundamental
+behavior of strategic nodes on the star. For example, as $p$ or $pi$
+get larger, the situations under which a strategic $Y$ type edge node
+might choose $N$ change. For low enough $\pi$ (on the star graph), $Y$
+type nodes will choose $N$ after only one edge node has chosen $N$. As
+$\pi$ rises, this stubbornness threshold also rises in discrete jumps
+as seen on the graph.
 
-Lastly, we investigate the computational complexity of our algorithm in Figure~\ref{fig:time} by measuring computation time over varied graph sizes.
-We time the star graph, which has one block that scales with $n$, and the cloud graph, which has two blocks that scale with $n$.
-As predicted, running time is quadratic for the star graph and quartic for the cloud graph.
+Lastly, we investigate the computational complexity of our algorithm
+in Figure~\ref{fig:time} by measuring computation time over varied
+graph sizes. We time the star graph, which has one block that scales
+with $n$, and the cloud graph, which has two blocks that scale with
+$n$. As predicted, running time is quadratic for the star graph and
+quartic for the cloud graph.
 
@@
 
-Talk about the significance, patterns, stuff like that that? Talk
-about future work in quantifying for general graphs, although it may
-not be possible?? At least in some nice form.
+Our results are interesting and certainly show that the difference
+between optimal play with myopic and strategic users is a complex
+space even very simple block graphs. However, there are still a number
+of interesting unexplored questions that we have not looked at in the
+scope of the problem.
 
-Patterns may not exist, but there may still be order level
-relationships / bounds that are possible.
+Despite the fact that obvious patterns don't exist in the performance
+ratio, it is still possible that the performance ratio can be bounded
+in certain circumstance beyond the star graph. Proving bounds on the
+performance ratio could help characterize the discontinuous regions in
+the plots where myopic superiority switches in favor of strategic
+agents.
 
-See if we can prove the problem is PPAD or NP-complete.
+We have only shown a polynomial time algorithm for graphs where the
+number of blocks is constant with respect to $N$. A further and
+important step would be to come up with an algorithm for general
+graphs, or to reduce the problem to another complexity class like PPAD
+or NP.
 
-Offline scheduling
-
-There are a number of possible extensions for this algorithm that
-should also broaden the class of graphs that our results could apply
-to. These extensions include scaling to $k$-block graphs, directed
-graphs, and stochastic block graphs. Extending the algorithm to
-$k$-block graphs shouldn’t conceptually change the algorithm, but we
-believe that the original algorithm may scale exponentially in $k$ for
-a $k$-block graph. However, for bounded $k$, the complexity is still
-be moderately efficient. Additionally, scaling the algorithm up to
-$k$-blocks may expose room for improvement in the algorithm and
-provide further insight into quantifying the difference between myopic
-and strategic agents in this setting. Modifying the algorithm to
-account for directed graphs as long as they still fit into a
-blockmodel is also likely trivial and would further increase the
-number of graphs that we can analyze theoretically although the
-applicability of directed graphs is not immediately apparent. Another
-potentially easy extension of this would be to look at stochastic
-blockmodels\cite{Wang87, Snijders97}. It seems reasonable that the
-algorithm for static block graph models might extend in expectation to
-unrealized (and hence offline scheduled) stochastic blockmodels. This
-extension could likely never extend to realized graphs or to online
-schedules, but stochastic blockmodels are much closer to graphs found
-experimentally than $k$-block graphs.
+The algorithm as it is presented only works for online
+scheduling. This is a necessary condition to allow the dynamic
+programming to work, however ongoing research may suggest that for
+offline scheduling, myopic agents will always permit a higher number
+of Yes nodes. Looking at performance bounds under offline scheduling
+could pose an viable avenue to study performance difference where
+online schedules became very complicated. It is not apparent how to
+compute an optimal offline schedule efficiently for a block graph or
+otherwise.
 

### 2012-12-12 paper.tex
Made small spelling/grammar changes

@@
 More specifically, we propose to research the impact of having
-strategic users: how much different are results if we assume users are
-strategic instead of myopic. To answer this question, we will use a
+strategic users: how different are results if we assume users are
+strategic instead of myopic? To answer this question, we will use a
 model introduced in \cite{Chierichetti12} and described in
-Section~\ref{prob_statement}. Our contribution is to fully
+Section~\ref{prob_statement}. Our contribution is to begin to
 characterize the behavior of this model on a specific class of graphs,
-the 2-blockmodels, in hopes of learning more about the general
+the blockmodels, in hopes of learning more about the general
 case. Blockmodels have been studied extensively in the past
@@
 games of this sort with their seminal work on graphical games
-\cite{Kearns01}. But, to the extent of our knowledge, nobody has
-attempted to characterize full graphical game models for cascade
+\cite{Kearns01}. But, to the best of our knowledge, nobody has
+attempted to solve graphical game models for cascade
 spreading.  This is what we do below.
@@
 We keep the same scheduler behavior as in the previous paper. The
-schedulers utility is based off of the number of nodes that choose Yes
+scheduler's utility is based off of the number of nodes that choose Yes
 at the end of the game. We assume the scheduler can change its plan
 after it sees what a node chooses. We also assume it has full
-knowledge of the nodes strategies, as well as knowledge of the full
+knowledge of the nodes' strategies, as well as knowledge of the full
 graph, and any game parameters. The only aspect the scheduler does not
-know is the individual nodes types.
+know is the individual node types.
 
-The nodes utility is the sum of all of their neighbors that match
+The nodes' utility is the sum of all of their neighbors that match
 their choice plus some constant ($\pi$) if their choice matches their
@@
 node is assigned Yes type ($p$), but not any other nodes type. To keep
-the model interesting, we restrict $p < 0.5$. Similarly myopic nodes
+the model interesting, we restrict $p < 0.5$. Conversely, myopic nodes
 only try to maximize their current utility, ignoring any nodes that
-has not made a decision.
+have not made a decision.
 
 We consider games where either all nodes in the graph are strategic or
-myopic, and want to see what graphs / game parameters contribute to
+all are myopic, and want to see what graphs / game parameters contribute to
 significant differences between the expected number of Yesses when
@@
 \end{align*}
-where $\mathbb I$ is the indicator function, and $N$ is the neighbor
+where $\mathbb I$ is the indicator function, and $N$ is the neighborhood
 function. The schedule function returns the next node to pick given
@@
 hard problem, but we will show an algorithm that can compute an
-optimal online schedule and calculate $\mathbb E[\#Y|stragetic]$ in
-polynomial time for arbitrary block models.
+optimal online schedule and calculate $\mathbb E[\#Y|stragetic]$ for arbitrary
+block models in time polynomial in the number of blocks.
 
@@
 is bounded by the polynomial time to compute both tables.\footnote{It
-  is possible that instead of looking these up on the fly, he table
+  is possible that instead of looking these up on the fly, the table
   could be precomputed to speed up the complexity slightly, but we
@@
 To determine the optimal block choice for the scheduler, the decision
-function only needs to know, ho many nodes from each block have
-already gone, and what proportion (or number) of the nodes have chosen
+function only needs to know how many nodes from each block have
+already gone and what proportion (or number) of the nodes have chosen
 Yes. Because nodes within a block are exchangeable, this information
@@
 each block conditioned on the node choosing Yes or No. The node then
-trivially calculates its expected utility for each choice, and picks
+trivially calculates its expected utility for each choice and picks
 the maximum.
@@
 
-Lookups are constant time, so the total time complexity is going to
-be bounded by the number of entries in the table times the number of
+Lookups are constant time, so the total time complexity is 
+ bounded by the number of entries in the table times the number of
 table lookups it takes to compute one entry in the table.
@@
 \begin{align*}
-  NodeTableSize &= o\left( 2k \prod_{i=1}^k s_i+1 \prod_{i=1}^k s_i+1
+  NodeTableSize &= O\left( 2k \prod_{i=1}^k s_i+1 \prod_{i=1}^k s_i+1
   \right) \\
-  &= o\left( k \prod_{i=1}^k s_i^2 \right)
+  &= O\left( k \prod_{i=1}^k s_i^2 \right)
   \intertext{If we further assume that $\ell \le k$ of
@@
     size of the table reduces to}
-  NodeTableSize &= o\left( kn^{2\ell} \right)
+  NodeTableSize &= O\left( kn^{2\ell} \right)
   \intertext{Each node table entry
@@
     table}
-  NodeTableComplexity &= o\left( k^2 \prod_{i=1}^k s_i^2 \right) \\
-  &= o\left( k^2 n^{2\ell} \right)
+  NodeTableComplexity &= O\left( k^2 \prod_{i=1}^k s_i^2 \right) \\
+  &= O\left( k^2 n^{2\ell} \right)
   \intertext{The size of the scheduler table is also trivial to upper
@@
     similar reasoning}
-  SchedTableSize &= o\left( \prod_{i=1}^k s_i+1 \prod_{i=1}^k s_i+1
+  SchedTableSize &= O\left( \prod_{i=1}^k s_i+1 \prod_{i=1}^k s_i+1
   \right) \\
-  &= o\left( \prod_{i=1}^k s_i^2 \right)
+  &= O\left( \prod_{i=1}^k s_i^2 \right)
   \intertext{If we make the same assumption about block sizes this
     reduces to}
-  SchedTableSize &= o \left( n^{2\ell} \right)
+  SchedTableSize &= O \left( n^{2\ell} \right)
   \intertext{The complexity for each entry in the scheduler table is
@@
     scheduler table is bounded by}
-  SchedTableComplexity &= o\left( k \prod_{i=1}^k s_i^2 \right) \\
-  &= o \left( k n^{2\ell} \right)
+  SchedTableComplexity &= O\left( k \prod_{i=1}^k s_i^2 \right) \\
+  &= O \left( k n^{2\ell} \right)
   \intertext{This leaves us with final time complexity of}
-  RunningTime &= o\left( k^2 \prod_{i=1}^k s_i^2 \right) \\
-  &= o\left( k^2 n^{2\ell} \right)
+  RunningTime &= O\left( k^2 \prod_{i=1}^k s_i^2 \right) \\
+  &= O\left( k^2 n^{2\ell} \right)
 \end{align*}
@@
 We have only shown a polynomial time algorithm for graphs where the
-number of blocks is constant with respect to $N$. A further and
+number of blocks is constant with respect to $n$. A further and
 important step would be to come up with an algorithm for general

### 2012-12-12 paper.tex
Added cloud graph, and minor changes

@@
 \title{Cascades, Product Conversion, Whatever}
-\author{T. Martian \& E. Brinkbot}
+\author{T. Martin \& E. Brinkman}
 
@@
 agent which makes a decision (e.g. to buy an iPod or to buy a Zune)
-and derives greater utility if his neighbors make the same
+and derives greater utility if her neighbors make the same
 decision. To the best of our knowledge, all current strategic agent
@@
 is a risk neutral rational agent. Each node is also assigned a binary
-type which affects their utility, pulled from a binomial
+type which affects their utility, sampled from a Bernoulli
 distribution. In this paper we call the types Yes ($Y$) and No
@@
 ``choice'' (also Yes or No) and the agent is committed to that
-``choice'' for the rest of the game. The game ends when all nodes have
-picked a ``choice.''
+choice for the rest of the game. The game ends when all nodes have
+picked a choice.
 
 We keep the same scheduler behavior as in the previous paper. The
-scheduler's utility is based off of the number of nodes that choose Yes
-at the end of the game. We assume the scheduler can change its plan
-after it sees what a node chooses. We also assume it has full
-knowledge of the nodes' strategies, as well as knowledge of the full
-graph, and any game parameters. The only aspect the scheduler does not
-know is the individual node types.
+scheduler's utility is maximized by maximizing the number of nodes
+that choose Yes at the end of the game. We assume the scheduler can
+change its plan after it sees what a node chooses. We also assume the
+scheduler has full knowledge of the nodes' strategies, as well as
+knowledge of the full graph, and any game parameters. The only aspect
+the scheduler does not know is the realized individual node types.
 
-The nodes' utility is the sum of all of their neighbors that match
-their choice plus some constant ($\pi$) if their choice matches their
-type. Strategic nodes make decisions to maximize their expected
-profit. We assume strategic nodes know the schedulers decision making
-(or utility function), the graph structure, and the probability that a
-node is assigned Yes type ($p$), but not any other nodes type. To keep
-the model interesting, we restrict $p < 0.5$. Conversely, myopic nodes
-only try to maximize their current utility, ignoring any nodes that
-have not made a decision.
+A node's utility is the sum of all of their neighbors that match their
+choice plus some constant ($\pi$) if their choice matches their
+type. Strategic nodes make decisions to maximize their expected profit
+at the end of the game. We assume strategic nodes know the scheduler's
+decision making (or utility function), the graph structure, and the
+probability that a node is assigned Yes type ($p$), but not any other
+node's type. To keep the model interesting, we restrict $p <
+0.5$. Conversely, myopic nodes only try to maximize their current
+utility, ignoring any nodes that have not made a decision.
 
 We consider games where either all nodes in the graph are strategic or
-all are myopic, and want to see what graphs / game parameters contribute to
-significant differences between the expected number of Yesses when
-nodes are strategic versus myopic.
+all are myopic, and want to see what graphs or game parameters
+contribute to significant differences between the expected number of
+Yeses when nodes are strategic versus myopic.
 
@@
   & t_i \in \{Y, N\} && \text{type of node $i$} \\
-  & p(t_i = Y) = p < 0.5 \\
+  & P(t_i = Y) = p < 0.5 \\
   & u_i(\mathbf c) = \pi \mathbb I[t_i = c_i] + \sum_{j \in N(i)}
@@
 
-The full game can be described by the following algorithm. The
-scheduler picks an optimal first node in the graph. That node chooses
-either Yes or No based on all of the parameters and its
-knowledge. Based on this result the scheduler picks a new node, and so
-on until every node has been picked and the game finishes.
+The full game can be described by the following algorithm.
+\begin{enumerate}
+\item \label{start} The scheduler picks an optimal node in the graph
+\item That node chooses either Yes or No based on all of the
+  parameters and its knowledge
+\item Repeat from step \ref{start} until all nodes have picked a
+  choice
+\end{enumerate}
 
@@
 Is seems likely that computing the strategic choices and payouts is a
-hard problem, but we will show an algorithm that can compute an
-optimal online schedule and calculate $\mathbb E[\#Y|stragetic]$ for arbitrary
-block models in time polynomial in the number of blocks.
+hard problem\footnote{We don't have a proof of this yet, but it is
+  interesting future work}, but we will show an algorithm that can
+compute an optimal online schedule and calculate $\mathbb
+E[\#Y|stragetic]$ for arbitrary blockmodels in time polynomial in the
+number of blocks.
 
-A graph is a $k$-block model if the vertices can be divided into $k$
+A graph is a $k$-blockmodel if the vertices can be divided into $k$
 disjoint subsets such that every node in the same subset has
@@
 
-An example of a 2-block model would be the star graph, which can be
+An example of a 2-blockmodel would be the star graph, which can be
 expressed in adjacency matrix form as
@@
 entries, where each entry is the choice, and the expected number of
-Yesses at the end of the game in each block conditioned on that
+Yeses at the end of the game in each block conditioned on that
 choice. If an entry is already calculated, then the lookup is constant
@@
 function only needs to know how many nodes from each block have
-already gone and what proportion (or number) of the nodes have chosen
-Yes. Because nodes within a block are exchangeable, this information
-completely characterizes the state of the game at the time of
-scheduler choice.
+already gone and how many of the nodes have chosen Yes. Because nodes
+within a block are exchangeable, this information completely
+characterizes the state of the game at the time of scheduler choice.
 
@@
 node possible to pick. It then marginalizes out the type of the node
-to calculate the expected number of Yesses for each choice of
+to calculate the expected number of Yeses for each choice of
 block. The optimal choice is simply the one that maximizes the
-expected number of Yesses.
+expected number of Yeses.
 
@@
 Yes or No, and choose the choice that maximizes it. The node can query
-the scheduler function to determine the expected number of Yesses in
+the scheduler function to determine the expected number of Yeses in
 each block conditioned on the node choosing Yes or No. The node then
@@
 
-Completely calculating the results of these functions is trivially
-simple, and in doing so completely finds the optimal online schedule
-and optimal node choice along that schedule.
+Completely calculating the results of these functions is simple, and
+in doing so computes the optimal online schedule and optimal
+node choice along that schedule.
+
+It is trivial to see that this algorithm can also solve the
+myopic case, as well as directed weighted arbitrary $k$-blockmodels.
 
@@
 
-See Section \ref{sec:algorithm} for an explanation of the algorithm.
-
-Lookups are constant time, so the total time complexity is 
+Lookups in the tables are constant time, so the total time complexity is 
  bounded by the number of entries in the table times the number of
@@
 We test a star graph, a clique, and a special graph we call a cloud
-graph. A cloud graph consists of two singular ``outer'' vertices of
+graph (See Figure~\ref{fig:cloud_graph}). A cloud graph consists of two singular ``outer'' vertices of
 degree $a$ and $b$ respectively, one singular ``inner'' vertex of
@@
 parameters, provably obtains more $Y$ adoptions for strategic users.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{cloud_graph.pdf}
+  \caption{Stylized Cloud Graph.}
+  \label{fig:cloud_graph}
+\end{figure}
 
@@
 
-Our results are interesting and certainly show that the difference
-between optimal play with myopic and strategic users is a complex
-space even very simple block graphs. However, there are still a number
-of interesting unexplored questions that we have not looked at in the
-scope of the problem.
+Our results show that the difference between optimal play with myopic
+and strategic users is a complex space even for very simple block
+graphs. However, there are still a number of interesting unexplored
+questions that we have not looked at in the scope of the problem.
 
-Despite the fact that obvious patterns don't exist in the performance
+Despite the fact that obvious patterns do not exist in the performance
 ratio, it is still possible that the performance ratio can be bounded
